### 2018-01-03 project/paper.tex
Initial commit.

\documentclass[12pt]{article}

% This first part of the file is called the PREAMBLE. It includes
% customizations and command definitions. The preamble is everything
% between \documentclass and \begin{document}.

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath,bm}            % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments
\usepackage{listings}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[linesnumbered,ruled,vlined,algosection]{algorithm2e}
\usepackage{parskip} 			   % no paragraph indentation

\usetikzlibrary{arrows,automata}

\input{include/Walgo.tex}

% various theorems, numbered by section

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{defi}[thm]{Definition}

\DeclareMathOperator{\id}{id}

\newcommand{\bd}[1]{\mathbf{#1}}  % for bolding symbols
\newcommand{\RR}{\mathbb{R}}      % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}}      % for Integers
\newcommand{\col}[1]{\left[\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}

\lstset{ % General setup for the package
    language={[LaTeX]TeX},
    basicstyle=\footnotesize\sffamily,
    tabsize=4,
    columns=fixed,
    keepspaces,
    commentstyle=\color{red},
    keywordstyle=\color{blue},
    xleftmargin=.1\textwidth,
    xrightmargin=.1\textwidth
}

\begin{document}

\nocite{*}

\title{Topics in Algorithms}

\author{Viktor Hansen \& Mehdi Nadif}

\maketitle

\begin{abstract}
  This comprises our project covering Approximation Distance Oracles with Improved Query Time for the Topics in Algorithms course offered at The Department of Computer Science, Uni. Copenhagen.
\end{abstract}

\pagebreak

\section{Overview}
Given an undirected, positively weighted graph $G$ with $m$ edges, $n$ vertices and given $k \in \mathbb{Z}$, $k \geq 2$, we show that a $2k-1$ approximate distance oracle for $G$ of size $O(kn^{1+1/k})$ and with $O(\lg k)$ query time can be constructed in $O( \min \left\{ kmn^{1/k}, \sqrt{k}m+kn^{1+c/\sqrt{k}} \right\})$ time for some constant $c$.

\section{Preliminaries}
\begin{itemize}
\item $d_{G}(u,v)$: the shortest path distance between $u$ and $v$.
\item $A_i = \left\{ a \in A_{i-1} \; | \; a \text{ sampled with prob. } n^{-1/k} \text{ uniformly, i.i.d.} \right\}$
\item $V = A_0 \supseteq A_1 \supseteq \hdots \supseteq A_k = \emptyset$
\item $p_i(u) = \min_{v \in A_i} \left\{ d_{G}(u,v) \right\}$
\item $B_u=\bigcup_{i=0}^{k-1}\left\{ v \in A_i - A_{i+1} \; | \; d_{G}(u,v) < d_{G}(u, p_{i+1}(u)) \right\}$
\item $d_G(u,p_k(u))=\infty$
\end{itemize}

\begin{lem}
Let $u,v \in V$ be distinct vertices $0 \leq i < k-1$. If $p_i(v) \not\in B_{u}$ then $d_G(u, p_{i+1}(u)) \leq d_G(u, p_i(v))$. Furthermore $A_{k-1} \subset B_u$ and $p_{k-1}(v) \in B_u$. \label{lem:onedeltaperiteration}
\end{lem}

\section{Oracle with $O(\lg k)$ query time}
\begin{Walgo}[ht]{20pt}
  \DontPrintSemicolon
  \SetKwRepeat{Do}{do}{while}
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \Indm
    \Indp
    \BlankLine
    $w \leftarrow p_i(u); j \leftarrow i$

    \While{$w \not\in B_v$}{
      $j \leftarrow j + 1$

      $(u,v) \leftarrow (v,u)$

      $w \leftarrow p_j(u)$
    }
    \Return{$d_G(w,u) + d_G(w,v)$}

    \caption{$dist_k(u,v,i)$}
    \label{alg:0.1}
\end{Walgo}

\begin{defi}
For vertices $u,v \in V$ an index $j \in \mathcal{I}$ is $(u,v)$-terminal if
\begin{enumerate}
\item $j = k-1$ or
\item $j < k-1$ is even and $p_j(u) \in B_v$ or $p_{j+1}(v) \in B_u$ 
\end{enumerate}
We note that $j$ attains a $(u,v)$ terminal index, the algorithm terminates in the current or next iteration.
\end{defi}

\begin{defi}
A subsequence $\mathcal{I'}=i_1, \hdots, i_2$ of $\mathcal{I}$ is $(u,v)$-feasible if
\begin{enumerate}
\item $i_1$ is even and
\item $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$ and
\item $i_2$ is $(u,v)$-terminal
\end{enumerate}
\end{defi}

\begin{lem}
Let $i_1, \hdots, i_2$ be a $(u,v)$-feasible subsequence. Then $dist_k(u,v,i_1)$ gives a $2k-1$ approximation of $d_G(u,v)$ in time $O(i_2-i_1)$.
\paragraph{Proof} By assumption $i_2$ is $(u,v)$-terminal. Therefore, $p_{i_2}(u) \in B_v$ or $p_{i_2 + 1}(v) \in B_u$. Thus $dist_k(u,v,i_1)$ terminates when $j=O(i_2)$ in time $O(i_2-i_1)$.

Furthermore $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$. When $p_j(u) = w \not\in B_v$
we have $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u)) \leq d_G(v,u) + d_G(u,p_j(u))$ by Lemma \ref{lem:onedeltaperiteration} and the triangle inequality. Hence each iteration of $dist_k(u,v,i)$ increases $d_G(u,w)$ by at most $d_G(u,v)$. At termination we have
\begin{align*}
d_G(u,w) + d_G(w,v) &\leq 2d_G(u,w) + d_G(u,v) \\
&\leq 2(i_1 \cdot d_G(u,v) + (i_2 - i_1)d_G(u,v)) + d_G(u,v) \\
&\leq 2 \cdot i_2 \cdot d_G(u,v) + d_G(u,v) \\
&\leq (2 \cdot i_2 + 1)d_G(u,v) \\
&\leq (2 (k-1) + 1)d_G(u,v) \\
&\leq (2k-1) d_G(u,v)
\end{align*}
\end{lem}

\end{document}

### 2018-01-08 project/paper.tex
Added comments.

@@
 \section{Overview}
+% Assumptions about the reader
+
+% Reference til Mikkel/Zwick paper - hans query time og 'vores' forbedrede query time - forbedring af konstruktion. Forbedring i querytime, uden at det påvirker space/konstruktionstid.
+
+% Motivation
+
+% Girth Conjecture?
+
 Given an undirected, positively weighted graph $G$ with $m$ edges, $n$ vertices and given $k \in \mathbb{Z}$, $k \geq 2$, we show that a $2k-1$ approximate distance oracle for $G$ of size $O(kn^{1+1/k})$ and with $O(\lg k)$ query time can be constructed in $O( \min \left\{ kmn^{1/k}, \sqrt{k}m+kn^{1+c/\sqrt{k}} \right\})$ time for some constant $c$.
-
-\section{Preliminaries}
+% Definitioner
 \begin{itemize}
@@
 \end{lem}
+% Inkluder illustration - forklarende tekst "By lemma 2.1 and the triangle inequality"
+
+% Lemma 3.2 her - Hele sekvensen, svarende til at køre Thorup-Zwick i=1...k
+
+% Lemma 3.3 her - "skip hver anden" - gør analysen symmetrisk - lav illustration (projicer punkter ned på reelle akse og indtegn afstande). Forklar bevis.
 

### 2018-01-08 project/paper.tex
Added binary search feasibility lemma.

@@
 
+\begin{lem}
+Let $i_1, \hdots, i_2$ be a $(u,v)$-feasible subsequence and let $i$ be even, $i_1+2 \leq i \leq i_2-2$.
+Let $j$ be an even index in subsequence $i_1, \hdots ,i-2$ that maximizes $\delta_j(u)$.
+If $p_j(u) \not\in B_v$ and $p_j+1(v) \not\in B_u$ then $i, \hdots , i_2$ is $(u,v)$-feasible.
+Otherwise, $i_1, \hdots , j$ is $(u,v)$-feasible.
+
+\paragraph{Proof} If $p_j(u) \in B_v$ or $p_j+1(v) \in B_u$, then $j$ is $(u,v)$-feasible, and so is $i_1, \hdots, j$.
+Assume that $p_j(u) \not\in B_v$ and $p_j+1(v) \not\in B_u$.
+Then, by Lemma \ref{lem:lemma1}, $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u))$ and $d_G(u,p_{j+2}(u)) \leq d_G(u,p_{j+1(v)})$.
+Applying the triangle inequality twice, we get
+\begin{align*}
+d_G(u,p_{j+2}(u) &\leq d_G(u,p_{j+1}(v)) \\
+&\leq d_G(u,v) + d_G(v, p_{j+1}(v)) \\
+&\leq d_G(u,v) + d_G(v, p_{j}(u)) \\
+&\leq 2d_G(u,v) + d_G(u, p_{j}(u))
+\end{align*}
+so $\delta_j(u) = d_G(u,p_{j+2}(u)) - d_G(u,p_j(u)) \leq 2d_G(u,v)$.
+Let $\mathcal{I}'$ be the set of even indices $i_1, i_1+2, i_1+4, \hdots, i-2$.
+Since $i_1, \hdots, i_2$ is $(u,v)$-feasible, $d_G(u,p_{i_1}(u)) \leq i_1 \cdot d_G(u,v)$.
+By the choice of $j$,
+\begin{align*}
+d_G(u,p_{i}(u)) &= d_G(u,p_{i_1}(u)) + \sum_{j' \in \mathcal{I'}}\delta_{j'}(u) \\
+&\leq d_G(u,p_{i_1}(u)) + \left| \mathcal{I'} \right| \max_{j' \in \mathcal{I'}}\delta_{j'}(u) \\
+&= d_G(u,p_{i_1}(u)) + \frac{i-i_1}{2} \delta_{j}(u) \\
+&\leq i_1 \cdot d_G(u,v) + (i-i_1)d_G(u,v) \\
+&= i \cdot d_G(u,v)
+\end{align*}
+Hence, since $i_1, \hdots, i_2$ is $(u,v)$-feasible, so is $i, \hdots, i_2$.
+\end{lem}
+
 \end{document}

### 2018-01-08 project/paper.tex
Added code for figure
Added second figure to figure to show delta increase

@@
 \usepackage{parskip} 			   % no paragraph indentation
+\usepackage{subcaption}
 
@@
 
+\begin{figure}
+\begin{subfigure}[b]{\textwidth}
+\begin{tikzpicture}
+\filldraw (0,0) circle (2pt) node[align=left,   below] {$u$};
+\filldraw (10,0) circle (2pt) node[align=right,  below] {$v$};
+\filldraw[fill=gray] (4,3) circle (2pt) node[align=left, above] {$p_j(u)$};
+\filldraw[fill=white] (8,3.45) circle (2pt) node[align=left, above] {$p_{j+1}(v)$};
+\coordinate (u) at (0,0) ;
+\coordinate (v) at (10,0);
+\coordinate (pu) at (4,3);
+\coordinate (pv) at (8, 3.45);
+\draw[dashed] (v) circle [radius=4];
+\draw (u) -- (pu) node[pos=0.5, above, sloped] {$d_G(u,p_j(u))$};
+\draw (u) -- (v) node[pos=0.5, below, sloped] {$d_G(u,v))$};
+\draw (v) -- (pv) node[pos=0.5, below, sloped] {$d_G(v, p_{j+1}(v)$};
+\draw[dotted] (v) -- (pu) node[pos=0.75, below, sloped] {$d_G(v, p_{j}(u)$};
+\end{tikzpicture}
+\caption{$(j)$th iteration\label{j1}}
+\end{subfigure}
+\begin{subfigure}[b]{\textwidth}
+\begin{tikzpicture}
+\filldraw (0,0) circle (2pt) node[align=left,   below] {$v$};
+\filldraw (10,0) circle (2pt) node[align=right,  below] {$u$};
+\filldraw[fill={rgb:black,1;white,3}] (5,4.9) circle (2pt) node[align=left, above] {$p_{j+2}(v)$};
+\filldraw[fill=white] (8,3.45) circle (2pt) node[align=left, above] {$p_{j+1}(u)$};
+\coordinate (v) at (0,0) ;
+\coordinate (u) at (10,0);
+\coordinate (pv) at (5,4.9);
+\coordinate (pu) at (8, 3.45);
+\begin{scope}
+    \clip (0,6) rectangle (7,-1);
+    \draw[dashed] (v) circle [radius=7];
+\end{scope}
+
+\draw (v) -- (pv) node[pos=0.5, above, sloped] {$d_G(v,p_{j+2}(v))$};
+\draw (v) -- (u) node[pos=0.5, below, sloped] {$d_G(v,u))$};
+\draw (u) -- (pu) node[pos=0.5, below, sloped] {$d_G(u, p_{j+1}(u)$};
+\draw[dotted] (v) -- (pu) node[pos=0.5, below, sloped] {$d_G(v, p_{j+1}(u)$};
+\end{tikzpicture}
+\caption{$(j+1)$th iteration.\label{j2}}
+\end{subfigure}
+\caption{Two consecutive iterations of the while loop in $dist_k$.
+Both sampled points of $u$, $p_j(u)$ in Fig.
+\ref{j1} and $p_{j+1}(u)$ in Fig.
+\ref{j2}, are not in $B_v$ and therefore $j$ is not $(u,v)$-terminal.}
+\end{figure}
 % Reference til Mikkel/Zwick paper - hans query time og 'vores' forbedrede query time - forbedring af konstruktion. Forbedring i querytime, uden at det påvirker space/konstruktionstid.

### 2018-01-10 project/paper.tex
Added tree struct

@@
 \usepackage{subcaption}
-
+\usepackage{pgfplots}
 \usetikzlibrary{arrows,automata}
@@
     xrightmargin=.1\textwidth
+}
+
+% argument #1: any options
+\newenvironment{customlegend}[1][]{%
+    \begingroup
+    % inits/clears the lists (which might be populated from previous
+    % axes):
+    \csname pgfplots@init@cleared@structures\endcsname
+    \pgfplotsset{#1}%
+}{%
+    % draws the legend:
+    \csname pgfplots@createlegend\endcsname
+    \endgroup
+}%
+\def\addlegendimage{\csname pgfplots@addlegendimage\endcsname}
+\pgfkeys{/pgfplots/number in legend/.style={%
+        /pgfplots/legend image code/.code={%
+            \node at (0.125,-0.0225){#1}; % <= changed x value
+        },%
+    },
+}
+\pgfplotsset{
+every legend to name picture/.style={west}
 }
@@
 
+\begin{figure}[H]
+\begin{tikzpicture}[level distance=1.5cm,
+  level 1/.style={sibling distance=3cm},
+  level 2/.style={sibling distance=1.5cm}]
+  \node[color=red] {$I'$}
+    child[color=red] {node {$[0, ..., n/2]$}
+    child[color=black,thick] {node[color=cyan] {$I^j$}}
+      child[dashed] {node {$p(l_1)$}
+      	child[solid, left=0.1cm, color=black] {node[color=cyan] {$l_1=[i_1, i_1+2]$}}
+      	child[solid,color=black] {node[color=cyan] {$[i_1+2,i_1+4]$}}
+      }
+    }
+    child[right=0.1cm, color=red] {node {$[n/2+2,...,n]$}
+    child[color=black] {node[color=cyan] {$I^k$} 
+    						child[dotted, color=black] {node {...}}
+    						child[dotted, color=black,left=0.1cm] {node {...}}
+    					}
+      child[dashed] {{node {$p(l_2)$}
+       	child[solid,color=black] {node[color=cyan] {$[i_2-4,i_2-2]$}}
+      	child[right=1cm,solid,color=black] {node[color=cyan] {$l_2=[i_2-2, i_2]$}}
+    }}};
+
+\begin{customlegend}[legend cell align=left, %<= to align cells
+legend entries={ % <= in the following there are the entries
+$P$: path between $p(l_1)$ and $p(l_2)$,
+ nodes belonging to $X$.
+},
+legend style={at={(0,2)},font=\footnotesize}] % <= to define position and font legend
+% the following are the "images" and numbers in the legend
+    \addlegendimage{solid,red}
+    \addlegendimage{area legend,cyan, fill=cyan}
+\end{customlegend}
+\end{tikzpicture}
+\caption{Lorem Ipsumthing}
+\end{figure}
+
 \end{document}

### 2018-01-10 project/paper.tex
Added distances on number line figure.

--- 2018-01-08 project/paper.tex
@@
 
-\usetikzlibrary{arrows,automata}
+\usetikzlibrary{arrows,automata,decorations.pathreplacing,math}
 
 \input{include/Walgo.tex}
+
+% various tikz defs
+\makeatletter
+\newcommand{\gettikzxy}[3]{%
+  \tikz@scan@one@point\pgfutil@firstofone#1\relax
+  \edef#2{\the\pgf@x}%
+  \edef#3{\the\pgf@y}%
+}
+\makeatother
 
@@
 
+\begin{figure}
+\centering
+\begin{tikzpicture}
+\filldraw (0,0) circle (2pt) node[align=left,   below] {$u$};
+\filldraw (10,0) circle (2pt) node[align=right,  below] {$v$};
+\filldraw[fill=gray] (4,3) circle (2pt) node[align=left, above] {$p_j(u)$};
+\filldraw[fill=gray] (8,3.5) circle (2pt) node[align=left, above] {$p_{j+1}(v)$};
+\coordinate (u) at (0,0) ;
+\coordinate (v) at (10,0);
+\coordinate (pu) at (4,3);
+\coordinate (pv) at (8, 3.5);
+\draw[dashed] (v) circle [radius=4];
+\draw (u) -- (pu) node[pos=0.5, above, sloped] {$d_G(u,p_j(u))$};
+\draw (u) -- (v) node[pos=0.5, below, sloped] {$d_G(u,v))$};
+\draw (v) -- (pv);
+\end{tikzpicture}
+\caption{Lorem Ipsumthing}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+\tikzmath{
+  \a = 3;
+  \b = 2;
+  \i0 = 0;
+  \i1 = 0*\a+\b;
+  \i2 = 0.75*\a+\b;
+  \i3 = 1.7*\a+\b;
+  \i4 = 2.5*\a+\b;
+  \i5 = 3.25*\a+\b;
+  \i6 = 4*\a+\b;
+  \s0 = 0;
+  \s1 = \s0 + \i1;
+  \s2 = \s1 + \i2;
+  \s3 = \s2 + \i3;
+  \s4 = \s3 + \i4;
+  \s5 = \s4 + \i5;
+  \s6 = \s5 + \i6;
+}
+
+%\draw[-latex] (0,0) -- (4.5*\a+\b,0);
+\draw[-] (0,0) -- (\i1*0.2,0);
+\draw[dashed] (\i1*0.2,0) -- (\i1-\i1*0.2,0);
+\draw[-] (\i1-\i1*0.2,0) -- (\i1,0);
+
+\draw[-] (\i1,0) -- (\i1+\i2*0.2-\i1*0.2,0);
+\draw[dashed] (\i1+\i2*0.2-\i1*0.2,0) -- (\i2-\i2*0.2+\i1*0.2,0);
+\draw[-] (\i2-\i2*0.2+\i1*0.2,0) -- (\i2,0);
+
+\draw[-,thick,red] (\i2,0) -- (\i3,0);
+
+\draw[-] (\i3,0) -- (\i3+\i4*0.2-\i3*0.2,0);
+\draw[dashed] (\i3+\i4*0.2-\i3*0.2,0) -- (\i4-\i4*0.2+\i3*0.2,0);
+\draw[-] (\i4-\i4*0.2+\i3*0.2,0) -- (\i4,0);
+
+\draw[-] (\i4,0) -- (\i5,0);
+
+\draw[-] (\i5,0) -- (\i5+\i6*0.2-\i5*0.2,0);
+\draw[dashed] (\i5+\i6*0.2-\i5*0.2,0) -- (\i6-\i6*0.2+\i5*0.2,0);
+\draw[-] (\i6-\i6*0.2+\i5*0.2,0) -- (\i6,0);
+
+\draw[-latex] (\i6,0) -- (\i6+1,0);
+
+% 0
+\draw[shift={(0,0)},color=black] (0pt,3pt) -- (0pt,-3pt);
+\draw[shift={(0,0)},color=black] (0pt,0pt) -- (0pt,-3pt) node[below] 
+{$0$};
+
+% p_i_1
+\draw[shift={(\i1,0)},color=black] (0pt,3pt) -- (0pt,-3pt);
+\draw[shift={(\i1,0)},color=black] (0pt,0pt) -- (0pt,-3pt) node[below] 
+{$d_G(p_{i_1}(u))$};
+
+% p_j
+\draw[shift={(\i2,0)},color=black] (0pt,3pt) -- (0pt,-3pt);
+\draw[shift={(\i2,0)},color=black] (0pt,0pt) -- (0pt,-3pt) node[below] 
+{$d_G(p_j(u))$};
+
+% p_j_p2
+\draw[shift={(\i3,0)},color=black] (0pt,3pt) -- (0pt,-3pt);
+\draw[shift={(\i3,0)},color=black] (0pt,0pt) -- (0pt,-3pt) node[below] 
+{$d_G(p_{j+2}(u))$};
+
+% p_i
+\draw[shift={(\i4,0)},color=black] (0pt,3pt) -- (0pt,-3pt);
+\draw[shift={(\i4,0)},color=black] (0pt,0pt) -- (0pt,-3pt) node[below] 
+{$d_G(p_{i-2}(u))$};
+
+% p_i_p2
+\draw[shift={(\i5,0)},color=black] (0pt,3pt) -- (0pt,-3pt);
+\draw[shift={(\i5,0)},color=black] (0pt,0pt) -- (0pt,-3pt) node[below] 
+{$d_G(p_{i}(u))$};
+
+% p_i_2
+\draw[shift={(\i6,0)},color=black] (0pt,3pt) -- (0pt,-3pt);
+\draw[shift={(\i6,0)},color=black] (0pt,0pt) -- (0pt,-3pt) node[below] 
+{$d_G(p_{i_2}(u))$};
+
+% d_G(u,p_{1_i}(u))
+\draw[decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt]
+(0,1.2) -- (\i1,1.2) node [black,midway,xshift=0cm,yshift=23pt] {\footnotesize
+$d_G(u,p_{i_1}(u))$};
+
+% \delta_j(u)
+\draw[decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
+(\i3,0.075) -- (\i2,0.075) node [black,midway,xshift=0cm,yshift=23pt] {\footnotesize
+$\delta_j(u)$};
+
+% \sum
+\draw[decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
+(\i5,1.2) -- (\i1,1.2) node [black,midway,xshift=0cm,yshift=23pt] {\footnotesize
+$\sum_{j' \in \mathcal{I}'}\delta_{j'}(u)$};
+
+\draw[dashed] (0,0) -- (0,1.2);
+\draw[dashed] (\i1,0) -- (\i1,1.2);
+\draw[dashed] (\i5,0) -- (\i5,1.2);
+
+\end{tikzpicture}
+\caption{Lorem Ipsumthing}
+\end{figure}
 % Reference til Mikkel/Zwick paper - hans query time og 'vores' forbedrede query time - forbedring af konstruktion. Forbedring i querytime, uden at det påvirker space/konstruktionstid.

### 2018-01-10 project/include/tikz/distance_real_line.tikz.tex

--- 2018-01-10 project/paper.tex
@@
-\documentclass[12pt]{article}
-
-% This first part of the file is called the PREAMBLE. It includes
-% customizations and command definitions. The preamble is everything
-% between \documentclass and \begin{document}.
-
-\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
-\usepackage{graphicx}              % to include figures
-\usepackage{amsmath,bm}            % great math stuff
-\usepackage{amsfonts}              % for blackboard bold, etc
-\usepackage{amsthm}                % better theorem environments
-\usepackage{listings}
-\usepackage{hyperref}
-\usepackage{tikz}
-\usepackage[linesnumbered,ruled,vlined,algosection]{algorithm2e}
-\usepackage{parskip} 			   % no paragraph indentation
-
-\usetikzlibrary{arrows,automata,decorations.pathreplacing,math}
-
-\input{include/Walgo.tex}
-
-% various tikz defs
-\makeatletter
-\newcommand{\gettikzxy}[3]{%
-  \tikz@scan@one@point\pgfutil@firstofone#1\relax
-  \edef#2{\the\pgf@x}%
-  \edef#3{\the\pgf@y}%
-}
-\makeatother
-
-% various theorems, numbered by section
-
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{conj}[thm]{Conjecture}
-\newtheorem{defi}[thm]{Definition}
-
-\DeclareMathOperator{\id}{id}
-
-\newcommand{\bd}[1]{\mathbf{#1}}  % for bolding symbols
-\newcommand{\RR}{\mathbb{R}}      % for Real numbers
-\newcommand{\ZZ}{\mathbb{Z}}      % for Integers
-\newcommand{\col}[1]{\left[\begin{matrix} #1 \end{matrix} \right]}
-\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
-
-\lstset{ % General setup for the package
-    language={[LaTeX]TeX},
-    basicstyle=\footnotesize\sffamily,
-    tabsize=4,
-    columns=fixed,
-    keepspaces,
-    commentstyle=\color{red},
-    keywordstyle=\color{blue},
-    xleftmargin=.1\textwidth,
-    xrightmargin=.1\textwidth
-}
-
-\begin{document}
-
-\nocite{*}
-
-\title{Topics in Algorithms}
-
-\author{Viktor Hansen \& Mehdi Nadif}
-
-\maketitle
-
-\begin{abstract}
-  This comprises our project covering Approximation Distance Oracles with Improved Query Time for the Topics in Algorithms course offered at The Department of Computer Science, Uni. Copenhagen.
-\end{abstract}
-
-\pagebreak
-
-\section{Overview}
-% Assumptions about the reader
-
-\begin{figure}
-\centering
-\begin{tikzpicture}
-\filldraw (0,0) circle (2pt) node[align=left,   below] {$u$};
-\filldraw (10,0) circle (2pt) node[align=right,  below] {$v$};
-\filldraw[fill=gray] (4,3) circle (2pt) node[align=left, above] {$p_j(u)$};
-\filldraw[fill=gray] (8,3.5) circle (2pt) node[align=left, above] {$p_{j+1}(v)$};
-\coordinate (u) at (0,0) ;
-\coordinate (v) at (10,0);
-\coordinate (pu) at (4,3);
-\coordinate (pv) at (8, 3.5);
-\draw[dashed] (v) circle [radius=4];
-\draw (u) -- (pu) node[pos=0.5, above, sloped] {$d_G(u,p_j(u))$};
-\draw (u) -- (v) node[pos=0.5, below, sloped] {$d_G(u,v))$};
-\draw (v) -- (pv);
-\end{tikzpicture}
-\caption{Lorem Ipsumthing}
-\end{figure}
-
-\begin{figure}
-\centering
 \begin{tikzpicture}
@@
 }
+
+% circles
+\begin{scope}
+  \clip (0,-1.5) rectangle (\i6+1,1.5);
+  \draw[dashed,green] (0,0) circle [radius=\i1];
+  \draw[dashed,green] (0,0) circle [radius=\i2];
+  \draw[dashed,green] (0,0) circle [radius=\i3];
+  \draw[dashed,green] (0,0) circle [radius=\i4];
+  \draw[dashed,green] (0,0) circle [radius=\i5];
+  \draw[dashed,green] (0,0) circle [radius=\i6];
+\end{scope}
 
@@
 \end{tikzpicture}
-\caption{Lorem Ipsumthing}
-\end{figure}
-% Reference til Mikkel/Zwick paper - hans query time og 'vores' forbedrede query time - forbedring af konstruktion. Forbedring i querytime, uden at det påvirker space/konstruktionstid.
-
-% Motivation
-
-% Girth Conjecture?
-
-Given an undirected, positively weighted graph $G$ with $m$ edges, $n$ vertices and given $k \in \mathbb{Z}$, $k \geq 2$, we show that a $2k-1$ approximate distance oracle for $G$ of size $O(kn^{1+1/k})$ and with $O(\lg k)$ query time can be constructed in $O( \min \left\{ kmn^{1/k}, \sqrt{k}m+kn^{1+c/\sqrt{k}} \right\})$ time for some constant $c$.
-% Definitioner
-\begin{itemize}
-\item $d_{G}(u,v)$: the shortest path distance between $u$ and $v$.
-\item $A_i = \left\{ a \in A_{i-1} \; | \; a \text{ sampled with prob. } n^{-1/k} \text{ uniformly, i.i.d.} \right\}$
-\item $V = A_0 \supseteq A_1 \supseteq \hdots \supseteq A_k = \emptyset$
-\item $p_i(u) = \min_{v \in A_i} \left\{ d_{G}(u,v) \right\}$
-\item $B_u=\bigcup_{i=0}^{k-1}\left\{ v \in A_i - A_{i+1} \; | \; d_{G}(u,v) < d_{G}(u, p_{i+1}(u)) \right\}$
-\item $d_G(u,p_k(u))=\infty$
-\end{itemize}
-
-\begin{lem}
-Let $u,v \in V$ be distinct vertices $0 \leq i < k-1$.
-If $p_i(v) \not\in B_{u}$ then $d_G(u, p_{i+1}(u)) \leq d_G(u, p_i(v))$.
-Furthermore $A_{k-1} \subset B_u$ and $p_{k-1}(v) \in B_u$.
-\label{lem:onedeltaperiteration}
-\end{lem}
-
-\section{Oracle with $O(\lg k)$ query time}
-\begin{Walgo}[ht]{20pt}
-  \DontPrintSemicolon
-  \SetKwRepeat{Do}{do}{while}
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \Indm
-    \Indp
-    \BlankLine
-    $w \leftarrow p_i(u); j \leftarrow i$
-
-    \While{$w \not\in B_v$}{
-      $j \leftarrow j + 1$
-
-      $(u,v) \leftarrow (v,u)$
-
-      $w \leftarrow p_j(u)$
-    }
-    \Return{$d_G(w,u) + d_G(w,v)$}
-
-    \caption{$dist_k(u,v,i)$}
-    \label{alg:0.1}
-\end{Walgo}
-
-\begin{defi}
-For vertices $u,v \in V$ an index $j \in \mathcal{I}$ is $(u,v)$-terminal if
-\begin{enumerate}
-\item $j = k-1$ or
-\item $j < k-1$ is even and $p_j(u) \in B_v$ or $p_{j+1}(v) \in B_u$ 
-\end{enumerate}
-We note that $j$ attains a $(u,v)$ terminal index, the algorithm terminates in the current or next iteration.
-\end{defi}
-
-\begin{defi}
-A subsequence $\mathcal{I'}=i_1, \hdots, i_2$ of $\mathcal{I}$ is $(u,v)$-feasible if
-\begin{enumerate}
-\item $i_1$ is even and
-\item $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$ and
-\item $i_2$ is $(u,v)$-terminal
-\end{enumerate}
-\end{defi}
-
-\begin{lem}
-Let $i_1, \hdots, i_2$ be a $(u,v)$-feasible subsequence. Then $dist_k(u,v,i_1)$ gives a $2k-1$ approximation of $d_G(u,v)$ in time $O(i_2-i_1)$.
-\paragraph{Proof} By assumption $i_2$ is $(u,v)$-terminal. Therefore, $p_{i_2}(u) \in B_v$ or $p_{i_2 + 1}(v) \in B_u$. Thus $dist_k(u,v,i_1)$ terminates when $j=O(i_2)$ in time $O(i_2-i_1)$.
-
-Furthermore $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$. When $p_j(u) = w \not\in B_v$
-we have $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u)) \leq d_G(v,u) + d_G(u,p_j(u))$ by Lemma \ref{lem:onedeltaperiteration} and the triangle inequality.
-Hence each iteration of $dist_k(u,v,i)$ increases $d_G(u,w)$ by at most $d_G(u,v)$.
-At termination we have
-\begin{align*}
-d_G(u,w) + d_G(w,v) &\leq 2d_G(u,w) + d_G(u,v) \\
-&\leq 2(i_1 \cdot d_G(u,v) + (i_2 - i_1)d_G(u,v)) + d_G(u,v) \\
-&\leq 2 \cdot i_2 \cdot d_G(u,v) + d_G(u,v) \\
-&\leq (2 \cdot i_2 + 1)d_G(u,v) \\
-&\leq (2 (k-1) + 1)d_G(u,v) \\
-&\leq (2k-1) d_G(u,v)
-\end{align*}
-\end{lem}
-% Inkluder illustration - forklarende tekst "By lemma 2.1 and the triangle inequality"
-
-% Lemma 3.2 her - Hele sekvensen, svarende til at køre Thorup-Zwick i=1...k
-
-% Lemma 3.3 her - "skip hver anden" - gør analysen symmetrisk - lav illustration (projicer punkter ned på reelle akse og indtegn afstande). Forklar bevis.
-
-\begin{lem}
-Let $i_1, \hdots, i_2$ be a $(u,v)$-feasible subsequence and let $i$ be even, $i_1+2 \leq i \leq i_2-2$.
-Let $j$ be an even index in subsequence $i_1, \hdots ,i-2$ that maximizes $\delta_j(u)$.
-If $p_j(u) \not\in B_v$ and $p_j+1(v) \not\in B_u$ then $i, \hdots , i_2$ is $(u,v)$-feasible.
-Otherwise, $i_1, \hdots , j$ is $(u,v)$-feasible.
-
-\paragraph{Proof} If $p_j(u) \in B_v$ or $p_j+1(v) \in B_u$, then $j$ is $(u,v)$-feasible, and so is $i_1, \hdots, j$.
-Assume that $p_j(u) \not\in B_v$ and $p_j+1(v) \not\in B_u$.
-Then, by Lemma \ref{lem:lemma1}, $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u))$ and $d_G(u,p_{j+2}(u)) \leq d_G(u,p_{j+1(v)})$.
-Applying the triangle inequality twice, we get
-\begin{align*}
-d_G(u,p_{j+2}(u) &\leq d_G(u,p_{j+1}(v)) \\
-&\leq d_G(u,v) + d_G(v, p_{j+1}(v)) \\
-&\leq d_G(u,v) + d_G(v, p_{j}(u)) \\
-&\leq 2d_G(u,v) + d_G(u, p_{j}(u))
-\end{align*}
-so $\delta_j(u) = d_G(u,p_{j+2}(u)) - d_G(u,p_j(u)) \leq 2d_G(u,v)$.
-Let $\mathcal{I}'$ be the set of even indices $i_1, i_1+2, i_1+4, \hdots, i-2$.
-Since $i_1, \hdots, i_2$ is $(u,v)$-feasible, $d_G(u,p_{i_1}(u)) \leq i_1 \cdot d_G(u,v)$.
-By the choice of $j$,
-\begin{align*}
-d_G(u,p_{i}(u)) &= d_G(u,p_{i_1}(u)) + \sum_{j' \in \mathcal{I'}}\delta_{j'}(u) \\
-&\leq d_G(u,p_{i_1}(u)) + \left| \mathcal{I'} \right| \max_{j' \in \mathcal{I'}}\delta_{j'}(u) \\
-&= d_G(u,p_{i_1}(u)) + \frac{i-i_1}{2} \delta_{j}(u) \\
-&\leq i_1 \cdot d_G(u,v) + (i-i_1)d_G(u,v) \\
-&= i \cdot d_G(u,v)
-\end{align*}
-Hence, since $i_1, \hdots, i_2$ is $(u,v)$-feasible, so is $i, \hdots, i_2$.
-\end{lem}
-
-\end{document}

### 2018-01-10 project/include/tikz/j1th_iteration.tikz.tex

\begin{tikzpicture}
  \filldraw (0,0) circle (2pt) node[align=left,   below] {$v$};
  \filldraw (10,0) circle (2pt) node[align=right,  below] {$u$};
  \filldraw[fill={rgb:black,1;white,3}] (5,4.9) circle (2pt) node[align=left, above] {$p_{j+2}(v)$};
  \filldraw[fill=white] (8,3.45) circle (2pt) node[align=left, above] {$p_{j+1}(u)$};
  \coordinate (v) at (0,0) ;
  \coordinate (u) at (10,0);
  \coordinate (pv) at (5,4.9);
  \coordinate (pu) at (8, 3.45);
  \begin{scope}
    \clip (0,6) rectangle (7,-1);
    \draw[dashed,green] (v) circle [radius=7];
  \end{scope}
  \draw (v) -- (pv) node[pos=0.5, above, sloped] {$d_G(v,p_{j+2}(v))$};
  \draw (v) -- (u) node[pos=0.5, below, sloped] {$d_G(v,u))$};
  \draw (u) -- (pu) node[pos=0.5, below, sloped] {$d_G(u, p_{j+1}(u)$};
  \draw[dotted] (v) -- (pu) node[pos=0.5, below, sloped] {$d_G(v, p_{j+1}(u)$};
\end{tikzpicture}

### 2018-01-10 project/include/tikz/jth_iteration.tikz.tex

--- 2018-01-08 project/paper.tex
@@
-\documentclass[12pt]{article}
-
-% This first part of the file is called the PREAMBLE. It includes
-% customizations and command definitions. The preamble is everything
-% between \documentclass and \begin{document}.
-
-\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
-\usepackage{graphicx}              % to include figures
-\usepackage{amsmath,bm}            % great math stuff
-\usepackage{amsfonts}              % for blackboard bold, etc
-\usepackage{amsthm}                % better theorem environments
-\usepackage{listings}
-\usepackage{hyperref}
-\usepackage{tikz}
-\usepackage[linesnumbered,ruled,vlined,algosection]{algorithm2e}
-\usepackage{parskip} 			   % no paragraph indentation
-\usepackage{subcaption}
-
-\usetikzlibrary{arrows,automata}
-
-\input{include/Walgo.tex}
-
-% various theorems, numbered by section
-
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{conj}[thm]{Conjecture}
-\newtheorem{defi}[thm]{Definition}
-
-\DeclareMathOperator{\id}{id}
-
-\newcommand{\bd}[1]{\mathbf{#1}}  % for bolding symbols
-\newcommand{\RR}{\mathbb{R}}      % for Real numbers
-\newcommand{\ZZ}{\mathbb{Z}}      % for Integers
-\newcommand{\col}[1]{\left[\begin{matrix} #1 \end{matrix} \right]}
-\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
-
-\lstset{ % General setup for the package
-    language={[LaTeX]TeX},
-    basicstyle=\footnotesize\sffamily,
-    tabsize=4,
-    columns=fixed,
-    keepspaces,
-    commentstyle=\color{red},
-    keywordstyle=\color{blue},
-    xleftmargin=.1\textwidth,
-    xrightmargin=.1\textwidth
-}
-
-\begin{document}
-
-\nocite{*}
-
-\title{Topics in Algorithms}
-
-\author{Viktor Hansen \& Mehdi Nadif}
-
-\maketitle
-
-\begin{abstract}
-  This comprises our project covering Approximation Distance Oracles with Improved Query Time for the Topics in Algorithms course offered at The Department of Computer Science, Uni. Copenhagen.
-\end{abstract}
-
-\pagebreak
-
-\section{Overview}
-% Assumptions about the reader
-
-\begin{figure}
-\begin{subfigure}[b]{\textwidth}
 \begin{tikzpicture}
@@
   \coordinate (pv) at (8, 3.45);
-\draw[dashed] (v) circle [radius=4];
+  \begin{scope}
+    \clip (0,6) rectangle (10,-1);
+    \draw[dashed,green] (v) circle [radius=4];
+  \end{scope}
   \draw (u) -- (pu) node[pos=0.5, above, sloped] {$d_G(u,p_j(u))$};
@@
   \draw (v) -- (pv) node[pos=0.5, below, sloped] {$d_G(v, p_{j+1}(v)$};
-\draw[dotted] (v) -- (pu) node[pos=0.75, below, sloped] {$d_G(v, p_{j}(u)$};
+  \draw[dotted] (v) -- (pu) node[pos=0.7, below, sloped] {$d_G(v, p_{j}(u)$};
 \end{tikzpicture}
-\caption{$(j)$th iteration\label{j1}}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-\begin{tikzpicture}
-\filldraw (0,0) circle (2pt) node[align=left,   below] {$v$};
-\filldraw (10,0) circle (2pt) node[align=right,  below] {$u$};
-\filldraw[fill={rgb:black,1;white,3}] (5,4.9) circle (2pt) node[align=left, above] {$p_{j+2}(v)$};
-\filldraw[fill=white] (8,3.45) circle (2pt) node[align=left, above] {$p_{j+1}(u)$};
-\coordinate (v) at (0,0) ;
-\coordinate (u) at (10,0);
-\coordinate (pv) at (5,4.9);
-\coordinate (pu) at (8, 3.45);
-\begin{scope}
-    \clip (0,6) rectangle (7,-1);
-    \draw[dashed] (v) circle [radius=7];
-\end{scope}
-
-\draw (v) -- (pv) node[pos=0.5, above, sloped] {$d_G(v,p_{j+2}(v))$};
-\draw (v) -- (u) node[pos=0.5, below, sloped] {$d_G(v,u))$};
-\draw (u) -- (pu) node[pos=0.5, below, sloped] {$d_G(u, p_{j+1}(u)$};
-\draw[dotted] (v) -- (pu) node[pos=0.5, below, sloped] {$d_G(v, p_{j+1}(u)$};
-\end{tikzpicture}
-\caption{$(j+1)$th iteration.\label{j2}}
-\end{subfigure}
-\caption{Two consecutive iterations of the while loop in $dist_k$.
-Both sampled points of $u$, $p_j(u)$ in Fig.
-\ref{j1} and $p_{j+1}(u)$ in Fig.
-\ref{j2}, are not in $B_v$ and therefore $j$ is not $(u,v)$-terminal.}
-\end{figure}
-% Reference til Mikkel/Zwick paper - hans query time og 'vores' forbedrede query time - forbedring af konstruktion. Forbedring i querytime, uden at det påvirker space/konstruktionstid.
-
-% Motivation
-
-% Girth Conjecture?
-
-Given an undirected, positively weighted graph $G$ with $m$ edges, $n$ vertices and given $k \in \mathbb{Z}$, $k \geq 2$, we show that a $2k-1$ approximate distance oracle for $G$ of size $O(kn^{1+1/k})$ and with $O(\lg k)$ query time can be constructed in $O( \min \left\{ kmn^{1/k}, \sqrt{k}m+kn^{1+c/\sqrt{k}} \right\})$ time for some constant $c$.
-% Definitioner
-\begin{itemize}
-\item $d_{G}(u,v)$: the shortest path distance between $u$ and $v$.
-\item $A_i = \left\{ a \in A_{i-1} \; | \; a \text{ sampled with prob. } n^{-1/k} \text{ uniformly, i.i.d.} \right\}$
-\item $V = A_0 \supseteq A_1 \supseteq \hdots \supseteq A_k = \emptyset$
-\item $p_i(u) = \min_{v \in A_i} \left\{ d_{G}(u,v) \right\}$
-\item $B_u=\bigcup_{i=0}^{k-1}\left\{ v \in A_i - A_{i+1} \; | \; d_{G}(u,v) < d_{G}(u, p_{i+1}(u)) \right\}$
-\item $d_G(u,p_k(u))=\infty$
-\end{itemize}
-
-\begin{lem}
-Let $u,v \in V$ be distinct vertices $0 \leq i < k-1$.
-If $p_i(v) \not\in B_{u}$ then $d_G(u, p_{i+1}(u)) \leq d_G(u, p_i(v))$.
-Furthermore $A_{k-1} \subset B_u$ and $p_{k-1}(v) \in B_u$.
-\label{lem:onedeltaperiteration}
-\end{lem}
-
-\section{Oracle with $O(\lg k)$ query time}
-\begin{Walgo}[ht]{20pt}
-  \DontPrintSemicolon
-  \SetKwRepeat{Do}{do}{while}
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \Indm
-    \Indp
-    \BlankLine
-    $w \leftarrow p_i(u); j \leftarrow i$
-
-    \While{$w \not\in B_v$}{
-      $j \leftarrow j + 1$
-
-      $(u,v) \leftarrow (v,u)$
-
-      $w \leftarrow p_j(u)$
-    }
-    \Return{$d_G(w,u) + d_G(w,v)$}
-
-    \caption{$dist_k(u,v,i)$}
-    \label{alg:0.1}
-\end{Walgo}
-
-\begin{defi}
-For vertices $u,v \in V$ an index $j \in \mathcal{I}$ is $(u,v)$-terminal if
-\begin{enumerate}
-\item $j = k-1$ or
-\item $j < k-1$ is even and $p_j(u) \in B_v$ or $p_{j+1}(v) \in B_u$ 
-\end{enumerate}
-We note that $j$ attains a $(u,v)$ terminal index, the algorithm terminates in the current or next iteration.
-\end{defi}
-
-\begin{defi}
-A subsequence $\mathcal{I'}=i_1, \hdots, i_2$ of $\mathcal{I}$ is $(u,v)$-feasible if
-\begin{enumerate}
-\item $i_1$ is even and
-\item $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$ and
-\item $i_2$ is $(u,v)$-terminal
-\end{enumerate}
-\end{defi}
-
-\begin{lem}
-Let $i_1, \hdots, i_2$ be a $(u,v)$-feasible subsequence. Then $dist_k(u,v,i_1)$ gives a $2k-1$ approximation of $d_G(u,v)$ in time $O(i_2-i_1)$.
-\paragraph{Proof} By assumption $i_2$ is $(u,v)$-terminal. Therefore, $p_{i_2}(u) \in B_v$ or $p_{i_2 + 1}(v) \in B_u$. Thus $dist_k(u,v,i_1)$ terminates when $j=O(i_2)$ in time $O(i_2-i_1)$.
-
-Furthermore $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$. When $p_j(u) = w \not\in B_v$
-we have $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u)) \leq d_G(v,u) + d_G(u,p_j(u))$ by Lemma \ref{lem:onedeltaperiteration} and the triangle inequality.
-Hence each iteration of $dist_k(u,v,i)$ increases $d_G(u,w)$ by at most $d_G(u,v)$.
-At termination we have
-\begin{align*}
-d_G(u,w) + d_G(w,v) &\leq 2d_G(u,w) + d_G(u,v) \\
-&\leq 2(i_1 \cdot d_G(u,v) + (i_2 - i_1)d_G(u,v)) + d_G(u,v) \\
-&\leq 2 \cdot i_2 \cdot d_G(u,v) + d_G(u,v) \\
-&\leq (2 \cdot i_2 + 1)d_G(u,v) \\
-&\leq (2 (k-1) + 1)d_G(u,v) \\
-&\leq (2k-1) d_G(u,v)
-\end{align*}
-\end{lem}
-% Inkluder illustration - forklarende tekst "By lemma 2.1 and the triangle inequality"
-
-% Lemma 3.2 her - Hele sekvensen, svarende til at køre Thorup-Zwick i=1...k
-
-% Lemma 3.3 her - "skip hver anden" - gør analysen symmetrisk - lav illustration (projicer punkter ned på reelle akse og indtegn afstande). Forklar bevis.
-
-\begin{lem}
-Let $i_1, \hdots, i_2$ be a $(u,v)$-feasible subsequence and let $i$ be even, $i_1+2 \leq i \leq i_2-2$.
-Let $j$ be an even index in subsequence $i_1, \hdots ,i-2$ that maximizes $\delta_j(u)$.
-If $p_j(u) \not\in B_v$ and $p_j+1(v) \not\in B_u$ then $i, \hdots , i_2$ is $(u,v)$-feasible.
-Otherwise, $i_1, \hdots , j$ is $(u,v)$-feasible.
-
-\paragraph{Proof} If $p_j(u) \in B_v$ or $p_j+1(v) \in B_u$, then $j$ is $(u,v)$-feasible, and so is $i_1, \hdots, j$.
-Assume that $p_j(u) \not\in B_v$ and $p_j+1(v) \not\in B_u$.
-Then, by Lemma \ref{lem:lemma1}, $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u))$ and $d_G(u,p_{j+2}(u)) \leq d_G(u,p_{j+1(v)})$.
-Applying the triangle inequality twice, we get
-\begin{align*}
-d_G(u,p_{j+2}(u) &\leq d_G(u,p_{j+1}(v)) \\
-&\leq d_G(u,v) + d_G(v, p_{j+1}(v)) \\
-&\leq d_G(u,v) + d_G(v, p_{j}(u)) \\
-&\leq 2d_G(u,v) + d_G(u, p_{j}(u))
-\end{align*}
-so $\delta_j(u) = d_G(u,p_{j+2}(u)) - d_G(u,p_j(u)) \leq 2d_G(u,v)$.
-Let $\mathcal{I}'$ be the set of even indices $i_1, i_1+2, i_1+4, \hdots, i-2$.
-Since $i_1, \hdots, i_2$ is $(u,v)$-feasible, $d_G(u,p_{i_1}(u)) \leq i_1 \cdot d_G(u,v)$.
-By the choice of $j$,
-\begin{align*}
-d_G(u,p_{i}(u)) &= d_G(u,p_{i_1}(u)) + \sum_{j' \in \mathcal{I'}}\delta_{j'}(u) \\
-&\leq d_G(u,p_{i_1}(u)) + \left| \mathcal{I'} \right| \max_{j' \in \mathcal{I'}}\delta_{j'}(u) \\
-&= d_G(u,p_{i_1}(u)) + \frac{i-i_1}{2} \delta_{j}(u) \\
-&\leq i_1 \cdot d_G(u,v) + (i-i_1)d_G(u,v) \\
-&= i \cdot d_G(u,v)
-\end{align*}
-Hence, since $i_1, \hdots, i_2$ is $(u,v)$-feasible, so is $i, \hdots, i_2$.
-\end{lem}
-
-\end{document}

### 2018-01-10 project/paper.tex

--- 2018-01-10 project/paper.tex
@@
 \usepackage{amsthm}                % better theorem environments
+\usepackage{breqn}
 \usepackage{listings}
@@
 \usepackage{tikz}
+\usepackage{tikzscale}
+\usepackage{pgfplots}
 \usepackage[linesnumbered,ruled,vlined,algosection]{algorithm2e}
 \usepackage{parskip} 			   % no paragraph indentation
+\usetikzlibrary{arrows,automata,decorations.pathreplacing,math,arrows,automata}
 \usepackage{subcaption}
-\usepackage{pgfplots}
-\usetikzlibrary{arrows,automata}
 
 \input{include/Walgo.tex}
+
+% various tikz defs
+\makeatletter
+\newcommand{\gettikzxy}[3]{%
+  \tikz@scan@one@point\pgfutil@firstofone#1\relax
+  \edef#2{\the\pgf@x}%
+  \edef#3{\the\pgf@y}%
+}
+\makeatother
 
@@
 \begin{abstract}
-  This comprises our project covering Approximation Distance Oracles with Improved Query Time for the Topics in Algorithms course offered at The Department of Computer Science, Uni. Copenhagen.
+  This comprises our project covering the first half of the paper "Approximation Distance Oracles with Improved Query Time" by Christian Wulff-Nilsen \cite{Wulff2013}.
+This project attempts to elaborate and provide intuition on the $\lg k$-query time improvement by providing explanations and visualisations of proofs.
 \end{abstract}
@@
 \section{Overview}
+Given an undirected graph $G$ with non-negative edge weights, $m$ edges, $n$ vertices and some $k \in \mathbb{Z} \geq 2$, Thorup and Zwick showed that a $(2k-1)$-approximate distance oracle for $G$ of size $O(kn^{1+1/k})$ and $O(k)$ query time can be constructed in $kmn^{1/k}$ expected time \cite{Thorup2005}.
+\cite{Wulff2013} improves this query time to $\lg k$, while preserving stretch, space and preprocessing time.
+% Specifically $O( \min \left\{ kmn^{1/k}, \sqrt{k}m+kn^{1+c/\sqrt{k}} \right\})$ time for some constant $c$.
+
+The reduction in query time is accomplished by performing binary search on the bunch structures described in \cite{Thorup2005} by uniquely determining at which level the bunch 
 % Assumptions about the reader
 
-\begin{figure}
-\begin{subfigure}[b]{\textwidth}
-\begin{tikzpicture}
-\filldraw (0,0) circle (2pt) node[align=left,   below] {$u$};
-\filldraw (10,0) circle (2pt) node[align=right,  below] {$v$};
-\filldraw[fill=gray] (4,3) circle (2pt) node[align=left, above] {$p_j(u)$};
-\filldraw[fill=white] (8,3.45) circle (2pt) node[align=left, above] {$p_{j+1}(v)$};
-\coordinate (u) at (0,0) ;
-\coordinate (v) at (10,0);
-\coordinate (pu) at (4,3);
-\coordinate (pv) at (8, 3.45);
-\draw[dashed] (v) circle [radius=4];
-\draw (u) -- (pu) node[pos=0.5, above, sloped] {$d_G(u,p_j(u))$};
-\draw (u) -- (v) node[pos=0.5, below, sloped] {$d_G(u,v))$};
-\draw (v) -- (pv) node[pos=0.5, below, sloped] {$d_G(v, p_{j+1}(v)$};
-\draw[dotted] (v) -- (pu) node[pos=0.75, below, sloped] {$d_G(v, p_{j}(u)$};
-\end{tikzpicture}
-\caption{$(j)$th iteration\label{j1}}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-\begin{tikzpicture}
-\filldraw (0,0) circle (2pt) node[align=left,   below] {$v$};
-\filldraw (10,0) circle (2pt) node[align=right,  below] {$u$};
-\filldraw[fill={rgb:black,1;white,3}] (5,4.9) circle (2pt) node[align=left, above] {$p_{j+2}(v)$};
-\filldraw[fill=white] (8,3.45) circle (2pt) node[align=left, above] {$p_{j+1}(u)$};
-\coordinate (v) at (0,0) ;
-\coordinate (u) at (10,0);
-\coordinate (pv) at (5,4.9);
-\coordinate (pu) at (8, 3.45);
-\begin{scope}
-    \clip (0,6) rectangle (7,-1);
-    \draw[dashed] (v) circle [radius=7];
-\end{scope}
-
-\draw (v) -- (pv) node[pos=0.5, above, sloped] {$d_G(v,p_{j+2}(v))$};
-\draw (v) -- (u) node[pos=0.5, below, sloped] {$d_G(v,u))$};
-\draw (u) -- (pu) node[pos=0.5, below, sloped] {$d_G(u, p_{j+1}(u)$};
-\draw[dotted] (v) -- (pu) node[pos=0.5, below, sloped] {$d_G(v, p_{j+1}(u)$};
-\end{tikzpicture}
-\caption{$(j+1)$th iteration.\label{j2}}
-\end{subfigure}
-\caption{Two consecutive iterations of the while loop in $dist_k$.
-Both sampled points of $u$, $p_j(u)$ in Fig.
-\ref{j1} and $p_{j+1}(u)$ in Fig.
-\ref{j2}, are not in $B_v$ and therefore $j$ is not $(u,v)$-terminal.}
-\end{figure}
 % Reference til Mikkel/Zwick paper - hans query time og 'vores' forbedrede query time - forbedring af konstruktion. Forbedring i querytime, uden at det påvirker space/konstruktionstid.
@@
 
-Given an undirected, positively weighted graph $G$ with $m$ edges, $n$ vertices and given $k \in \mathbb{Z}$, $k \geq 2$, we show that a $2k-1$ approximate distance oracle for $G$ of size $O(kn^{1+1/k})$ and with $O(\lg k)$ query time can be constructed in $O( \min \left\{ kmn^{1/k}, \sqrt{k}m+kn^{1+c/\sqrt{k}} \right\})$ time for some constant $c$.
-% Definitioner
+\section{Definitions}
+The following definitions are taken directly from \cite{Thorup2005} and \cite{Wulff2013} and are used throughout this project.
 \begin{itemize}
@@
 \item $p_i(u) = \min_{v \in A_i} \left\{ d_{G}(u,v) \right\}$
-\item $B_u=\bigcup_{i=0}^{k-1}\left\{ v \in A_i - A_{i+1} \; | \; d_{G}(u,v) < d_{G}(u, p_{i+1}(u)) \right\}$
+\item $B_u=\bigcup_{i=0}^{k-1}\left\{ v \in A_i - A_{i+1} \; | \; d_{G}(u,v) < d_{G}(u, p_{i+1}(u)) \right\}$, the bunch of $u$.
 \item $d_G(u,p_k(u))=\infty$
 \end{itemize}
-
+Thorup and Zwick showed that
+\\
 \begin{lem}
@@
 Assume that $p_j(u) \not\in B_v$ and $p_j+1(v) \not\in B_u$.
-Then, by Lemma \ref{lem:lemma1}, $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u))$ and $d_G(u,p_{j+2}(u)) \leq d_G(u,p_{j+1(v)})$.
-Applying the triangle inequality twice, we get
+Then, by Lemma \ref{lem:onedeltaperiteration}, $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u))$ and $d_G(u,p_{j+2}(u)) \leq d_G(u,p_{j+1(v)})$.
+Applying the triangle inequality twice, cfr.
+Fig.
+\ref{fig:twoiterations}, we get
 \begin{align*}
-d_G(u,p_{j+2}(u) &\leq d_G(u,p_{j+1}(v)) \\
-&\leq d_G(u,v) + d_G(v, p_{j+1}(v)) \\
-&\leq d_G(u,v) + d_G(v, p_{j}(u)) \\
-&\leq 2d_G(u,v) + d_G(u, p_{j}(u))
+d_G(u,p_{j+2}(u) &\leq d_G(u,p_{j+1}(v)) &(\text{Lemma \ref{lem:onedeltaperiteration}}) \\
+&\leq d_G(u,v) + d_G(v, p_{j+1}(v)) &(\text{Triangle Inequality})\\
+&\leq d_G(u,v) + d_G(v, p_{j}(u)) &(\text{Lemma \ref{lem:onedeltaperiteration}})\\
+&\leq 2d_G(u,v) + d_G(u, p_{j}(u))&(\text{Triangle Inequality})
 \end{align*}
@@
 \end{align*}
-Hence, since $i_1, \hdots, i_2$ is $(u,v)$-feasible, so is $i, \hdots, i_2$.
+Hence, since $i_1, \hdots, i_2$ is $(u,v)$-feasible, so is $i, \hdots, i_2$.  \label{lem:uvfeasibility}
 \end{lem}
 
-\begin{figure}[H]
+\begin{figure}[!hbt]
+  \centering
+  \subcaptionbox{$(j)$th iteration\label{fig:j1}}{
+    \includegraphics[width=.45\textwidth]{include/tikz/jth_iteration.tikz}%
+  }
+  \hfill
+  \subcaptionbox{$(j+1)$th iteration\label{fig:j2}}{
+    \includegraphics[width=.45\textwidth]{include/tikz/j1th_iteration.tikz}%
+  }
+  \caption{Two consecutive iterations of the while loop in $dist_k$.
+Both sampled points of $u$, $p_j(u)$ in Fig.
+\ref{fig:j1} and $p_{j+1}(u)$ in Fig.
+\ref{fig:j2}, are not in $B_v$ and therefore $j$ is not $(u,v)$-terminal.
+An upper bound of $2d_{G}(u,v)+d_G(u,p_j(u))$ is derived on $d_G(u,p_{j+2}(u))$ in Lemma \ref{lem:uvfeasibility} by applying Lemma \ref{lem:onedeltaperiteration} and the triangle inequality twice.
+\label{fig:twoiterations}}
+\end{figure}
+
+\begin{figure}
+\centering
+    \includegraphics[width=1\textwidth]{include/tikz/distance_real_line.tikz}%
+\caption{Visualization of the distance $d_G(u,p_j(u))$ and $\delta_j(u)$.
+The green lines correspond to the circles defined by $u$ and the radii $d_G(p_l(u))$ for $l \in \left\{ i_1, j, j+2, i-2, i, i_2 \right\}$.}
+\end{figure}
+
+\begin{figure}[h]
 \begin{tikzpicture}[level distance=1.5cm,
@@
 
+\bibliographystyle{plain}
+\bibliography{bibliography}
+
 \end{document}

### 2018-01-10 project/paper.tex
Added description for tree structure and started on theorem 1.

@@
   \node[color=red] {$I'$}
-    child[color=red] {node {$[0, ..., n/2]$}
+    child[color=red] {node {$[0, ..., i]$}
     child[color=black,thick] {node[color=cyan] {$I^j$}}
@@
     }
-    child[right=0.1cm, color=red] {node {$[n/2+2,...,n]$}
+    child[right=0.1cm, color=red] {node {$[i,...,k-1]$}
     child[color=black] {node[color=cyan] {$I^k$} 
@@
 \end{tikzpicture}
-\caption{Lorem Ipsumthing}
+\caption{A tree $T_u$ representing the recursion of $bdist_k$ of $u$, each node corresponding to the interval of a recursive call.
+The root node $I'$ consists of all even indices between $0$ and $k-1$.\label{tree}}
 \end{figure}
 
+\begin{thm}
+For an integer $k\geq 2$, a $(2k - 1)$-approximate distance oracle of G of size $O(kn^{1+1/k})$ and $O(\log k)$ query time can be constructed in $O\left( \min \left\lbrace kmn^{1+\frac{1}{k}}, \sqrt{k}m + kn^{1+c/k}\right\rbrace\right)$ time for some constant $c$.
+\end{thm}
+{\it Proof.} For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
+The remaining preprocessing for $u$ is determining the necessary subsequences of $\mathcal{I}$ and the $j$ that maximized $\delta_j(u)$ for each subsequence.
+The necessary subsequences are built
+
+To bound the time to identify these desired $j$, a simple linear search requires $O(k\log k)$ time.
+This can be improved to $O(k)$ by constructing of a recursive tree $\mathcal{T}_u$ for each $u$ that represents the recursion of $bdist_k$ on the subsequence $\mathcal{I}'$ consisting of all even numbers in $\mathcal{I}$.
+A bottom-up seach of $\mathcal{T}_u$ can identify for each canonical subsequence (canonical meaning it is a node in $\mathcal{T}$) $i_1,i_1+2,...,i_2$ an index $j$ in the subsequence that maximizes $\delta_j(u)$ in $O(k)$ time.
+The bottom-up traversal of $T$ requires checking at most $O(\log k)$ subsequences; consider the subsequence $i_1,..,i_2$ in seperate leaf nodes as seen in Fig.
+\ref{tree}.
+The path $P$ (red) starting in $p(l_1)$ and ending in $p(l_2)$ has $O(\log k)$ children, which we denote $X$.
+The union of $X$ clearly covers the entire subsequence $i_1,i_1+2,...,i_2-2,i_2$, and finding a $j$ that maximizes $\delta_j(u)$ in $X$ therefore gives a $j$ that maximizes $\delta_j(u)$ in the subsequence $i_1,...,i_2$.
+If $j$ is known for each node in $\mathcal{T}$, it follows that finding the desired $j$ for any canonical subsequences is bound by $O(\log k)$\\
+
+The recursion tree for $bdist_k$ for $u$ will have $\theta(k/\log k)$ children and $\theta(k/\log k)$ non-child nodes.
+Computing $j$ for each subsequence in $T$ will take $O(\log k)$ time per node, so total preprocessing time for $u$ is $O(k)$.
 \bibliographystyle{plain}

### 2018-01-10 project/include/tikz/lemma1.tikz.tex
asd

--- 2018-01-10 project/include/tikz/jth_iteration.tikz.tex
@@
   \filldraw (10,0) circle (2pt) node[align=right,  below] {$v$};
-  \filldraw[fill=gray] (4,3) circle (2pt) node[align=left, above] {$p_j(u)$};
-  \filldraw[fill=white] (8,3.45) circle (2pt) node[align=left, above] {$p_{j+1}(v)$};
+  \filldraw[fill=gray] (4,3) circle (2pt) node[align=left, above] {$p_i(u)$};
+  \filldraw[fill=white] (8,3.45) circle (2pt) node[align=left, above] {$p_{i+1}(v)$};
   \coordinate (u) at (0,0) ;
@@
   \begin{scope}
-    \clip (0,6) rectangle (10,-1);
-    \draw[dashed,green] (v) circle [radius=4];
+    \clip (0,6) rectangle (7,-1);
+    \draw[dashed,green] (u) circle [radius=5];
   \end{scope}
-  \draw (u) -- (pu) node[pos=0.5, above, sloped] {$d_G(u,p_j(u))$};
+  \draw (u) -- (pu) node[pos=0.5, above, sloped] {$d_G(u,p_i(u))$};
   \draw (u) -- (v) node[pos=0.5, below, sloped] {$d_G(u,v))$};
-  \draw (v) -- (pv) node[pos=0.5, below, sloped] {$d_G(v, p_{j+1}(v)$};
-  \draw[dotted] (v) -- (pu) node[pos=0.7, below, sloped] {$d_G(v, p_{j}(u)$};
+  \draw (v) -- (pv) node[pos=0.5, below, sloped] {$d_G(v, p_{i+1}(v)$};
 \end{tikzpicture}

### 2018-01-10 project/paper.tex
asd

--- 2018-01-10 project/paper.tex
@@
 \section{Overview}
-Given an undirected graph $G$ with non-negative edge weights, $m$ edges, $n$ vertices and some $k \in \mathbb{Z} \geq 2$, Thorup and Zwick showed that a $(2k-1)$-approximate distance oracle for $G$ of size $O(kn^{1+1/k})$ and $O(k)$ query time can be constructed in $kmn^{1/k}$ expected time \cite{Thorup2005}.
+Given an undirected graph $G$ with non-negative edge weights, $m$ edges, $n$ vertices and some $k \in \mathbb{Z} \geq 2$, Thorup and Zwick showed that a $(2k-1)$-approximate distance oracle for $G$ of size $O(kn^{1+1/k})$ and $O(k)$ query time can be constructed in $O(kmn^{1/k})$ expected time \cite{Thorup2005}.
 \cite{Wulff2013} improves this query time to $\lg k$, while preserving stretch, space and preprocessing time.
@@
 
-The reduction in query time is accomplished by performing binary search on the bunch structures described in \cite{Thorup2005} by uniquely determining at which level the bunch 
+The query time reduction is made possible by observing that binary search can be performed on the iteration sequence of the $dist_k(u)$ algorithm described in \cite{Thorup2005}.
+This is done by precomputing a secondary data structures $\mathcal{T}_u$ for each $u \in V$ in $O(k)$ time.
+Each $\mathcal{T}_u$ contains information about which subsequences of $0, \hdots, k-1$ that make the modified $dist_k(u,i)$ algorithm (see Alg.
+\ref{alg:distk}) terminate while maintaining a  stretch of $(2k-1)$.
+Such subsequences are called $(u,v)$-feasible.
+Specifically, the subsequences in $T_u$ are \textit{canonical}.
+$(u,v)$-feasibility and canonicity is defined and discussed in 3.
+
 % Assumptions about the reader
 
-% Reference til Mikkel/Zwick paper - hans query time og 'vores' forbedrede query time - forbedring af konstruktion. Forbedring i querytime, uden at det påvirker space/konstruktionstid.
-
-% Motivation
-
-% Girth Conjecture?
-
 \section{Definitions}
-The following definitions are taken directly from \cite{Thorup2005} and \cite{Wulff2013} and are used throughout this project.
+The following definitions taken directly from \cite{Thorup2005} and \cite{Wulff2013} are used throughout this project and are listed here for brevity and coherency:
 \begin{itemize}
@@
 \item $A_i = \left\{ a \in A_{i-1} \; | \; a \text{ sampled with prob. } n^{-1/k} \text{ uniformly, i.i.d.} \right\}$
-\item $V = A_0 \supseteq A_1 \supseteq \hdots \supseteq A_k = \emptyset$
+\item $(V = A_0) \supseteq A_1 \supseteq \hdots \supseteq (A_k = \emptyset)$
 \item $p_i(u) = \min_{v \in A_i} \left\{ d_{G}(u,v) \right\}$
@@
 \end{itemize}
-Thorup and Zwick showed that
+Thorup and Zwick showed the property about bunches seen in Lemma \ref{lem:onedeltaperiteration}.
+The lemma is visualized in Fig.
+\ref{fig:lemma1vis}, and follows from the definitions of bunches.
+That $A_{k-1} \subset B_u$ and $p_{k-1}(v) \in B_u$ also readily follows from the definition of $A_{k}$ and $d_G(u,p_k(u))$ shown above:
 \\
@@
 \end{lem}
+This lemma is readily used for bounding $d_G(u,v)$ by successively applying the triangle inequality at each iteration of $dist_k(u,v)$ to arrive at the $(2k-1)$-stretch bound in \cite{Thorup2005}.
+
+\begin{figure}[!hbt]
+\centering
+    \includegraphics[width=0.5\textwidth]{include/tikz/lemma1.tikz}%
+\caption{Visualization of Lemma \ref{lem:onedeltaperiteration}.
+The dotted green path corresponds to the circle defined by $u$ and the radii $d_G(p_i(u))$, which $p_{i+1}(v)$ is clearly outside.
+\label{fig:lemma1vis}}
+\end{figure}
 
 \section{Oracle with $O(\lg k)$ query time}
+As aforementioned, binary search on the iteration sequence of the Thorup-Zwick oracle is performed to drive down the query time to $\lg k$.
+Starting with the iteration sequence $\mathcal{I}=1,\hdots,k-1$, the idea is to identify $r=O(\lg k)$ subsequences $(\mathcal{I}_1=\mathcal{I}) \supset \mathcal{I}_1 \supset \hdots \supset \mathcal{I}_r$, where for $2 \leq j \leq t$ we have $|\mathcal{I}_{j-1}| \geq 2|\mathcal{I}_j|$.
+We wish to maintain the invariant that $dist_k(u,v,i)$ applied to the first element of any subsequence $\mathcal{I}_j$ outputs the stretch $(2k-1)$ estimate in $|\mathcal{\mathcal{I}_j}|$ time.
+\\
+\begin{defi}
+For vertices $u,v \in V$ an index $j \in \mathcal{I}$ is $(u,v)$-terminal if
+\begin{enumerate}
+\item $j = k-1$ or
+\item $j < k-1$ is even and $p_j(u) \in B_v$ or $p_{j+1}(v) \in B_u$ 
+\end{enumerate}
+We note that $j$ attains a $(u,v)$ terminal index, the algorithm terminates in the current or next iteration. \label{def:uvterm}
+\end{defi}
+The definition of $(u,v)$-terminality captures the essence of when $dist_k(u,v)$ terminates, i.e.
+when $p_j(u) \in B_v$.
+This happens either when 1) $j=k-1$, in which case, trivially, $p_{k-1}(u) \in B_v$ or 2) when $j < k-1$ is even and $p_j(u) \in B_v$ or $p_{j+1}(v) \in B_u$ (in this case $dist_k(u,v)$ terminates either in iteration $j$ or $j+1$), see Alg.
+\ref{alg:distk}.
+\\
+\begin{defi}
+A subsequence $\mathcal{I'}=i_1, \hdots, i_2$ of $\mathcal{I}$ is $(u,v)$-feasible if
+\begin{enumerate}
+\item $i_1$ is even and
+\item $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$ and
+\item $i_2$ is $(u,v)$-terminal
+\end{enumerate}
+\label{def:uvfeas}
+\end{defi}
+Furthermore, the definition of $(u,v)$-feasibility
+
 \begin{Walgo}[ht]{20pt}
@@
     \caption{$dist_k(u,v,i)$}
-    \label{alg:0.1}
+    \label{alg:distk}
 \end{Walgo}
 
-\begin{defi}
-For vertices $u,v \in V$ an index $j \in \mathcal{I}$ is $(u,v)$-terminal if
-\begin{enumerate}
-\item $j = k-1$ or
-\item $j < k-1$ is even and $p_j(u) \in B_v$ or $p_{j+1}(v) \in B_u$ 
-\end{enumerate}
-We note that $j$ attains a $(u,v)$ terminal index, the algorithm terminates in the current or next iteration.
-\end{defi}
+\begin{Walgo}[ht]{20pt}
+  \DontPrintSemicolon
+  \SetKwRepeat{Do}{do}{while}
+  \SetKwInOut{Input}{Input}
+  \SetKwInOut{Output}{Output}
+  \Indm
+    \Indp
+    \BlankLine
+    \If{$i_2-i_1 \leq \lg k$}{
+    	\Return{$dist_k(u,v,i_1)$}
+	}
 
-\begin{defi}
-A subsequence $\mathcal{I'}=i_1, \hdots, i_2$ of $\mathcal{I}$ is $(u,v)$-feasible if
-\begin{enumerate}
-\item $i_1$ is even and
-\item $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$ and
-\item $i_2$ is $(u,v)$-terminal
-\end{enumerate}
-\end{defi}
+    \textbf{let} $i$ be the middle even index $i_1,\hdots,i_2$
+
+    \textbf{let} $i$ be the (precomputed) even index in $i_1,\hdots,i-2$ maximizing $\delta_j(u)$
+
+    \If{$p_j(u) \not\in B_v$ \textbf{and} $p_{j+1} \not\in B_u$}{
+    	\Return{$bdist_k(u,v,i,i_2)$}
+    }
+    \Else{
+    	\Return{$bdist_k(u,v,i_1,j)$}
+    }
+    \caption{$bdist_k(u,v,i_1,i_2)$}
+    \label{alg:bdistk}
+\end{Walgo}
 

### 2018-01-10 project/paper.tex
Moved algs to bottom.

@@
 Starting with the iteration sequence $\mathcal{I}=1,\hdots,k-1$, the idea is to identify $r=O(\lg k)$ subsequences $(\mathcal{I}_1=\mathcal{I}) \supset \mathcal{I}_1 \supset \hdots \supset \mathcal{I}_r$, where for $2 \leq j \leq t$ we have $|\mathcal{I}_{j-1}| \geq 2|\mathcal{I}_j|$.
-We wish to maintain the invariant that $dist_k(u,v,i)$ applied to the first element of any subsequence $\mathcal{I}_j$ outputs the stretch $(2k-1)$ estimate in $|\mathcal{\mathcal{I}_j}|$ time.
+We wish to maintain the invariant that $dist_k(u,v,i)$ applied to the first element of any subsequence $\mathcal{I}_j$ outputs the stretch $(2k-1)$ estimate in $|\mathcal{I}_j|$ time.
 \\
@@
 \end{defi}
-Furthermore, the definition of $(u,v)$-feasibility
-
-\begin{Walgo}[ht]{20pt}
-  \DontPrintSemicolon
-  \SetKwRepeat{Do}{do}{while}
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \Indm
-    \Indp
-    \BlankLine
-    $w \leftarrow p_i(u); j \leftarrow i$
-
-    \While{$w \not\in B_v$}{
-      $j \leftarrow j + 1$
-
-      $(u,v) \leftarrow (v,u)$
-
-      $w \leftarrow p_j(u)$
-    }
-    \Return{$d_G(w,u) + d_G(w,v)$}
-
-    \caption{$dist_k(u,v,i)$}
-    \label{alg:distk}
-\end{Walgo}
-
-\begin{Walgo}[ht]{20pt}
-  \DontPrintSemicolon
-  \SetKwRepeat{Do}{do}{while}
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \Indm
-    \Indp
-    \BlankLine
-    \If{$i_2-i_1 \leq \lg k$}{
-    	\Return{$dist_k(u,v,i_1)$}
-	}
-
-    \textbf{let} $i$ be the middle even index $i_1,\hdots,i_2$
-
-    \textbf{let} $i$ be the (precomputed) even index in $i_1,\hdots,i-2$ maximizing $\delta_j(u)$
-
-    \If{$p_j(u) \not\in B_v$ \textbf{and} $p_{j+1} \not\in B_u$}{
-    	\Return{$bdist_k(u,v,i,i_2)$}
-    }
-    \Else{
-    	\Return{$bdist_k(u,v,i_1,j)$}
-    }
-    \caption{$bdist_k(u,v,i_1,i_2)$}
-    \label{alg:bdistk}
-\end{Walgo}
+Condition $1$ and $3$ of $(u,v)$-feasibility entails a symmetric view of $dist_k(u,v,i)$ in which $u$ and $v$ successively exhanges roles for even an uneven $j$.
+Condition $2$ ensures that $dist_k(u,v,i)$ returns a $(2k-1)$-approximation when run with the first  $(u,v)$-feasible subsequence, as seen in the following lemma:
 
@@
 Computing $j$ for each subsequence in $T$ will take $O(\log k)$ time per node, so total preprocessing time for $u$ is $O(k)$.
+
+\begin{Walgo}[ht]{20pt}
+  \DontPrintSemicolon
+  \SetKwRepeat{Do}{do}{while}
+  \SetKwInOut{Input}{Input}
+  \SetKwInOut{Output}{Output}
+  \Indm
+    \Indp
+    \BlankLine
+    $w \leftarrow p_i(u); j \leftarrow i$
+
+    \While{$w \not\in B_v$}{
+      $j \leftarrow j + 1$
+
+      $(u,v) \leftarrow (v,u)$
+
+      $w \leftarrow p_j(u)$
+    }
+    \Return{$d_G(w,u) + d_G(w,v)$}
+
+    \caption{$dist_k(u,v,i)$}
+    \label{alg:distk}
+\end{Walgo}
+
+\begin{Walgo}[ht]{20pt}
+  \DontPrintSemicolon
+  \SetKwRepeat{Do}{do}{while}
+  \SetKwInOut{Input}{Input}
+  \SetKwInOut{Output}{Output}
+  \Indm
+    \Indp
+    \BlankLine
+    \If{$i_2-i_1 \leq \lg k$}{
+    	\Return{$dist_k(u,v,i_1)$}
+	}
+
+    \textbf{let} $i$ be the middle even index $i_1,\hdots,i_2$
+
+    \textbf{let} $i$ be the (precomputed) even index in $i_1,\hdots,i-2$ maximizing $\delta_j(u)$
+
+    \If{$p_j(u) \not\in B_v$ \textbf{and} $p_{j+1} \not\in B_u$}{
+    	\Return{$bdist_k(u,v,i,i_2)$}
+    }
+    \Else{
+    	\Return{$bdist_k(u,v,i_1,j)$}
+    }
+    \caption{$bdist_k(u,v,i_1,i_2)$}
+    \label{alg:bdistk}
+\end{Walgo}
+
 \bibliographystyle{plain}

### 2018-01-10 project/paper.tex
Theorem apsidj

--- 2018-01-10 project/paper.tex
@@
 \section{Overview}
-Given an undirected graph $G$ with non-negative edge weights, $m$ edges, $n$ vertices and some $k \in \mathbb{Z} \geq 2$, Thorup and Zwick showed that a $(2k-1)$-approximate distance oracle for $G$ of size $O(kn^{1+1/k})$ and $O(k)$ query time can be constructed in $O(kmn^{1/k})$ expected time \cite{Thorup2005}.
+Given an undirected graph $G$ with non-negative edge weights, $m$ edges, $n$ vertices and some $k \in \mathbb{Z} \geq 2$, Thorup and Zwick showed that a $(2k-1)$-approximate distance oracle for $G$ of size $O(kn^{1+1/k})$ and $O(k)$ query time can be constructed in $kmn^{1/k}$ expected time \cite{Thorup2005}.
 \cite{Wulff2013} improves this query time to $\lg k$, while preserving stretch, space and preprocessing time.
@@
 
-The query time reduction is made possible by observing that binary search can be performed on the iteration sequence of the $dist_k(u)$ algorithm described in \cite{Thorup2005}.
-This is done by precomputing a secondary data structures $\mathcal{T}_u$ for each $u \in V$ in $O(k)$ time.
-Each $\mathcal{T}_u$ contains information about which subsequences of $0, \hdots, k-1$ that make the modified $dist_k(u,i)$ algorithm (see Alg.
-\ref{alg:distk}) terminate while maintaining a  stretch of $(2k-1)$.
-Such subsequences are called $(u,v)$-feasible.
-Specifically, the subsequences in $T_u$ are \textit{canonical}.
-$(u,v)$-feasibility and canonicity is defined and discussed in 3.
-
+The reduction in query time is accomplished by performing binary search on the bunch structures described in \cite{Thorup2005} by uniquely determining at which level the bunch 
 % Assumptions about the reader
 
+% Reference til Mikkel/Zwick paper - hans query time og 'vores' forbedrede query time - forbedring af konstruktion. Forbedring i querytime, uden at det påvirker space/konstruktionstid.
+
+% Motivation
+
+% Girth Conjecture?
+
 \section{Definitions}
-The following definitions taken directly from \cite{Thorup2005} and \cite{Wulff2013} are used throughout this project and are listed here for brevity and coherency:
+The following definitions are taken directly from \cite{Thorup2005} and \cite{Wulff2013} and are used throughout this project.
 \begin{itemize}
@@
 \item $A_i = \left\{ a \in A_{i-1} \; | \; a \text{ sampled with prob. } n^{-1/k} \text{ uniformly, i.i.d.} \right\}$
-\item $(V = A_0) \supseteq A_1 \supseteq \hdots \supseteq (A_k = \emptyset)$
+\item $V = A_0 \supseteq A_1 \supseteq \hdots \supseteq A_k = \emptyset$
 \item $p_i(u) = \min_{v \in A_i} \left\{ d_{G}(u,v) \right\}$
@@
 \end{itemize}
-Thorup and Zwick showed the property about bunches seen in Lemma \ref{lem:onedeltaperiteration}.
-The lemma is visualized in Fig.
-\ref{fig:lemma1vis}, and follows from the definitions of bunches.
-That $A_{k-1} \subset B_u$ and $p_{k-1}(v) \in B_u$ also readily follows from the definition of $A_{k}$ and $d_G(u,p_k(u))$ shown above:
+Thorup and Zwick showed that
 \\
@@
 \end{lem}
-This lemma is readily used for bounding $d_G(u,v)$ by successively applying the triangle inequality at each iteration of $dist_k(u,v)$ to arrive at the $(2k-1)$-stretch bound in \cite{Thorup2005}.
-
-\begin{figure}[!hbt]
-\centering
-    \includegraphics[width=0.5\textwidth]{include/tikz/lemma1.tikz}%
-\caption{Visualization of Lemma \ref{lem:onedeltaperiteration}.
-The dotted green path corresponds to the circle defined by $u$ and the radii $d_G(p_i(u))$, which $p_{i+1}(v)$ is clearly outside.
-\label{fig:lemma1vis}}
-\end{figure}
 
 \section{Oracle with $O(\lg k)$ query time}
-As aforementioned, binary search on the iteration sequence of the Thorup-Zwick oracle is performed to drive down the query time to $\lg k$.
-Starting with the iteration sequence $\mathcal{I}=1,\hdots,k-1$, the idea is to identify $r=O(\lg k)$ subsequences $(\mathcal{I}_1=\mathcal{I}) \supset \mathcal{I}_1 \supset \hdots \supset \mathcal{I}_r$, where for $2 \leq j \leq t$ we have $|\mathcal{I}_{j-1}| \geq 2|\mathcal{I}_j|$.
-We wish to maintain the invariant that $dist_k(u,v,i)$ applied to the first element of any subsequence $\mathcal{I}_j$ outputs the stretch $(2k-1)$ estimate in $|\mathcal{\mathcal{I}_j}|$ time.
-\\
-\begin{defi}
-For vertices $u,v \in V$ an index $j \in \mathcal{I}$ is $(u,v)$-terminal if
-\begin{enumerate}
-\item $j = k-1$ or
-\item $j < k-1$ is even and $p_j(u) \in B_v$ or $p_{j+1}(v) \in B_u$ 
-\end{enumerate}
-We note that $j$ attains a $(u,v)$ terminal index, the algorithm terminates in the current or next iteration. \label{def:uvterm}
-\end{defi}
-The definition of $(u,v)$-terminality captures the essence of when $dist_k(u,v)$ terminates, i.e.
-when $p_j(u) \in B_v$.
-This happens either when 1) $j=k-1$, in which case, trivially, $p_{k-1}(u) \in B_v$ or 2) when $j < k-1$ is even and $p_j(u) \in B_v$ or $p_{j+1}(v) \in B_u$ (in this case $dist_k(u,v)$ terminates either in iteration $j$ or $j+1$), see Alg.
-\ref{alg:distk}.
-\\
-\begin{defi}
-A subsequence $\mathcal{I'}=i_1, \hdots, i_2$ of $\mathcal{I}$ is $(u,v)$-feasible if
-\begin{enumerate}
-\item $i_1$ is even and
-\item $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$ and
-\item $i_2$ is $(u,v)$-terminal
-\end{enumerate}
-\label{def:uvfeas}
-\end{defi}
-Furthermore, the definition of $(u,v)$-feasibility
-
 \begin{Walgo}[ht]{20pt}
@@
     \caption{$dist_k(u,v,i)$}
-    \label{alg:distk}
+    \label{alg:0.1}
 \end{Walgo}
 
-\begin{Walgo}[ht]{20pt}
-  \DontPrintSemicolon
-  \SetKwRepeat{Do}{do}{while}
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \Indm
-    \Indp
-    \BlankLine
-    \If{$i_2-i_1 \leq \lg k$}{
-    	\Return{$dist_k(u,v,i_1)$}
-	}
+\begin{defi}
+For vertices $u,v \in V$ an index $j \in \mathcal{I}$ is $(u,v)$-terminal if
+\begin{enumerate}
+\item $j = k-1$ or
+\item $j < k-1$ is even and $p_j(u) \in B_v$ or $p_{j+1}(v) \in B_u$ 
+\end{enumerate}
+We note that $j$ attains a $(u,v)$ terminal index, the algorithm terminates in the current or next iteration.
+\end{defi}
 
-    \textbf{let} $i$ be the middle even index $i_1,\hdots,i_2$
-
-    \textbf{let} $i$ be the (precomputed) even index in $i_1,\hdots,i-2$ maximizing $\delta_j(u)$
-
-    \If{$p_j(u) \not\in B_v$ \textbf{and} $p_{j+1} \not\in B_u$}{
-    	\Return{$bdist_k(u,v,i,i_2)$}
-    }
-    \Else{
-    	\Return{$bdist_k(u,v,i_1,j)$}
-    }
-    \caption{$bdist_k(u,v,i_1,i_2)$}
-    \label{alg:bdistk}
-\end{Walgo}
+\begin{defi}
+A subsequence $\mathcal{I'}=i_1, \hdots, i_2$ of $\mathcal{I}$ is $(u,v)$-feasible if
+\begin{enumerate}
+\item $i_1$ is even and
+\item $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$ and
+\item $i_2$ is $(u,v)$-terminal
+\end{enumerate}
+\end{defi}
 
@@
 Furthermore $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$. When $p_j(u) = w \not\in B_v$
-we have $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u)) \leq d_G(v,u) + d_G(u,p_j(u))$ by Lemma \ref{lem:onedeltaperiteration} and the triangle inequality.
+we have $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u)) \leq d_G(v,u) + d_G(u,p_j(u))$ by Lemma \ref{lem:onedeltaperiteration} and the triangle inequality, as visualized in Fig.
+\ref{fig:j1}.
 Hence each iteration of $dist_k(u,v,i)$ increases $d_G(u,w)$ by at most $d_G(u,v)$.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 \begin{tikzpicture}[level distance=1.5cm,
@@
 For an integer $k\geq 2$, a $(2k - 1)$-approximate distance oracle of G of size $O(kn^{1+1/k})$ and $O(\log k)$ query time can be constructed in $O\left( \min \left\lbrace kmn^{1+\frac{1}{k}}, \sqrt{k}m + kn^{1+c/k}\right\rbrace\right)$ time for some constant $c$.
-\end{thm}
-{\it Proof.} For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
+
+\paragraph{Proof.} For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
 The remaining preprocessing for $u$ is determining the necessary subsequences of $\mathcal{I}$ and the $j$ that maximized $\delta_j(u)$ for each subsequence.
-The necessary subsequences are built
+The necessary subsequences are built by
 
@@
 Computing $j$ for each subsequence in $T$ will take $O(\log k)$ time per node, so total preprocessing time for $u$ is $O(k)$.
+\end{thm}
 \bibliographystyle{plain}

### 2018-01-10 project/paper.tex

--- 2018-01-10 project/paper.tex
@@
 Computing $j$ for each subsequence in $T$ will take $O(\log k)$ time per node, so total preprocessing time for $u$ is $O(k)$.
+\end{thm}
 

### 2018-01-10 project/paper.tex
Extended the proof to Theorem 1

@@
 
-\paragraph{Proof.} For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
+\paragraph{Proof.}
+
+For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
 The remaining preprocessing for $u$ is determining the necessary subsequences of $\mathcal{I}$ and the $j$ that maximized $\delta_j(u)$ for each subsequence.
-The necessary subsequences are built by
+For a subsequence $I'=i_1,...i_2$, the necessary subsequences are constructed by finding an even index $i$ that equally splits $I'$ into two sets $i_1,...,i$ and $i,...,i_2$.
+Then, find a $j$ in $i_1,...,i$ that maximized $\delta_j(u)$.
+Then recurse on $i_1,...,i$ and $i,...,i_2$.
+The recursion stop when a subsequence has length at most $\log k$.
+This recursion corresponds to the recursion of $bdist_k$, and it will henceforth be referred to as the recursion of $bdist_k$.
 
+The query time is bounded by the number of recursions needed before reaching a $(u,v)-feasible$ subsequence of size at most $\log k$.
+$bdist_k$ uses a binary search, in which $\mathcal{I}$ is halved in size at each recursion and only one of the halves is recursed upon.
+As the height of the tree is $O(\log k)$ and $i$ and $j$ are known for all subsequences, the query time is $O(\log k)$.
 To bound the time to identify these desired $j$, a simple linear search requires $O(k\log k)$ time.
@@
 Computing $j$ for each subsequence in $T$ will take $O(\log k)$ time per node, so total preprocessing time for $u$ is $O(k)$.
+Thus, the preprocessing time for finding $j$ for $G$ is $O(nk)\leq O(km)\leq O(kmn^{1/k})$ as desired.
 \end{thm}

### 2018-01-10 project/paper.tex
Added theorem

@@
 The query time is bounded by the number of recursions needed before reaching a $(u,v)-feasible$ subsequence of size at most $\log k$.
-$bdist_k$ uses a binary search, in which $\mathcal{I}$ is halved in size at each recursion and only one of the halves is recursed upon.
-As the height of the tree is $O(\log k)$ and $i$ and $j$ are known for all subsequences, the query time is $O(\log k)$.
+$bdist_k$ uses a binary search, so that at an arbitraty iteration the subsequence will be split in half into subsequences $i_1,...,i$ and $i,...,i_2$.
+Only the one of these two subsequences that is $(u,v)$-terminal is then recursed upon.
+As the number of recursions in this binary search is $O(\log k)$ and $i$ and $j$ are known for all subsequences, the query time is $O(\log k)$.
 To bound the time to identify these desired $j$, a simple linear search requires $O(k\log k)$ time.

### 2018-01-10 project/paper.tex
lala

--- 2018-01-10 project/paper.tex
@@
 \end{defi}
-Condition $1$ and $3$ of $(u,v)$-feasibility entails a symmetric view of $dist_k(u,v,i)$ in which $u$ and $v$ successively exhanges roles for even an uneven $j$.
+Condition $1$ and $3$ of $(u,v)$-feasibility employs a symmetric view of iterations of $dist_k(u,v,i)$ in which $u$ and $v$ successively exhanges roles for even an uneven $j$.
 Condition $2$ ensures that $dist_k(u,v,i)$ returns a $(2k-1)$-approximation when run with the first $(u,v)$-feasible subsequence, as seen in the following lemma:
-
+\\
 \begin{lem}
@@
 Furthermore $d_{G}(p_{i_1}(u),u) \leq i_1 \cdot d_G(u,v)$. When $p_j(u) = w \not\in B_v$
-we have $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u)) \leq d_G(v,u) + d_G(u,p_j(u))$ by Lemma \ref{lem:onedeltaperiteration} and the triangle inequality, as visualized in Fig.
-\ref{fig:j1}.
+we have $d_G(v,p_{j+1}(v)) \leq d_G(v,p_{j}(u)) \leq d_G(v,u) + d_G(u,p_j(u))$ by Lemma \ref{lem:onedeltaperiteration} and the triangle inequality.
 Hence each iteration of $dist_k(u,v,i)$ increases $d_G(u,w)$ by at most $d_G(u,v)$.
@@
 \end{align*}
+\label{lem:uvfeasterminates}
 \end{lem}
-% Inkluder illustration - forklarende tekst "By lemma 2.1 and the triangle inequality"
 
-% Lemma 3.2 her - Hele sekvensen, svarende til at køre Thorup-Zwick i=1...k
-
-% Lemma 3.3 her - "skip hver anden" - gør analysen symmetrisk - lav illustration (projicer punkter ned på reelle akse og indtegn afstande). Forklar bevis.
-
+Furthermore the lemma shows that $dist_k(u,v,i)$ runs in time proportional to $i_2-i_1$. We also have the following ``base case'' for $\mathcal{I}$:
+\\
+\begin{lem}
+$\mathcal{I}$ is $(u,v)$-feasible for all $u,v \in V$. \label{lem:basecase}
+\end{lem}
+The above lemma follows since $p_{k-1}(u) \in B_v$ for all $u \not= v \in V$.
+The following lemma gives us a way of splitting a $(u,v)$-feasible subsequence $I$ into two subsequences of size roughly $\frac{1}{2}|\mathcal{I}|$:
+\\
 \begin{lem}
@@
 \end{lem}
+Visualisations of the proof for the bound on $d_G(u,p_{j+2})$ across two iterations can be seen in Fig.
+\ref{fig:twoiterations}.
+A visualisation of the proof for the bound on $d_G(u,p_i(u))$ can be seen Fig.
+\ref{fig:realline}.
 
@@
 \caption{Visualization of the distance $d_G(u,p_j(u))$ and $\delta_j(u)$.
-The green lines correspond to the circles defined by $u$ and the radii $d_G(p_l(u))$ for $l \in \left\{ i_1, j, j+2, i-2, i, i_2 \right\}$.}
+The green lines correspond to the circles defined by $u$ and the radii $d_G(p_l(u))$ for $l \in \left\{ i_1, j, j+2, i-2, i, i_2 \right\}$.
+\label{fig:realline}}
 \end{figure}
 
-\begin{figure}[H]
+What lemmas \ref{lem:uvfeasterminates}, \ref{lem:basecase} and \ref{lem:uvfeasibility} entail is that, starting with the $(u,v)$-feasible sequence $\mathcal{I}=0,\hdots,k-1$, we may split it into two subsequences, one in which $(u,v)$-feasibility must be preserved.
+This splitting can be done recursively until a subsequence $\mathcal{I_r}$ for which $|\mathcal{I_r}|=O(\lg k)$ is determined.
+Applying $dist_k(u,v,i)$ to the first element of $\mathcal{I_r}$ produces a $(2k-1)$-approximation of the distance from $u$ to $v$ by $(u,v)$-feasibility in time proportional to $|\mathcal{I}_r|=O(\lg k)$.
+
+\begin{figure}[h]
 \begin{tikzpicture}[level distance=1.5cm,
@@
 For an integer $k\geq 2$, a $(2k - 1)$-approximate distance oracle of G of size $O(kn^{1+1/k})$ and $O(\log k)$ query time can be constructed in $O\left( \min \left\lbrace kmn^{1+\frac{1}{k}}, \sqrt{k}m + kn^{1+c/k}\right\rbrace\right)$ time for some constant $c$.
-
-\paragraph{Proof.} For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
+\end{thm}
+{\it Proof.} For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
 The remaining preprocessing for $u$ is determining the necessary subsequences of $\mathcal{I}$ and the $j$ that maximized $\delta_j(u)$ for each subsequence.
-The necessary subsequences are built by
+The necessary subsequences are built
 
@@
 Computing $j$ for each subsequence in $T$ will take $O(\log k)$ time per node, so total preprocessing time for $u$ is $O(k)$.
-\end{thm}
 

### 2018-01-10 project/paper.tex

@@
 For an integer $k\geq 2$, a $(2k - 1)$-approximate distance oracle of G of size $O(kn^{1+1/k})$ and $O(\log k)$ query time can be constructed in $O\left( \min \left\lbrace kmn^{1+\frac{1}{k}}, \sqrt{k}m + kn^{1+c/k}\right\rbrace\right)$ time for some constant $c$.
-\end{thm}
-{\it Proof.} For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
+
+\paragraph{Proof.}
+
+For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
 The remaining preprocessing for $u$ is determining the necessary subsequences of $\mathcal{I}$ and the $j$ that maximized $\delta_j(u)$ for each subsequence.
-The necessary subsequences are built
+For a subsequence $I'=i_1,...i_2$, the necessary subsequences are constructed by finding an even index $i$ that equally splits $I'$ into two sets $i_1,...,i$ and $i,...,i_2$.
+Then, find a $j$ in $i_1,...,i$ that maximized $\delta_j(u)$.
+Then recurse on $i_1,...,i$ and $i,...,i_2$.
+The recursion stop when a subsequence has length at most $\log k$.
+This recursion corresponds to the recursion of $bdist_k$, and it will henceforth be referred to as the recursion of $bdist_k$.
 
+The query time is bounded by the number of recursions needed before reaching a $(u,v)-feasible$ subsequence of size at most $\log k$.
+$bdist_k$ uses a binary search, so that at an arbitraty iteration the subsequence will be split in half into subsequences $i_1,...,i$ and $i,...,i_2$.
+Only the one of these two subsequences that is $(u,v)$-terminal is then recursed upon.
+As the number of recursions in this binary search is $O(\log k)$ and $i$ and $j$ are known for all subsequences, the query time is $O(\log k)$.
 To bound the time to identify these desired $j$, a simple linear search requires $O(k\log k)$ time.
@@
 Computing $j$ for each subsequence in $T$ will take $O(\log k)$ time per node, so total preprocessing time for $u$ is $O(k)$.
+Thus, the preprocessing time for finding $j$ for $G$ is $O(nk)\leq O(km)\leq O(kmn^{1/k})$ as desired.
+\end{thm}
 

### 2018-01-14 project/paper.tex
asdasd

@@
 
-The query time reduction is made possible by observing that binary search can be performed on the iteration sequence of the $dist_k(u)$ algorithm described in \cite{Thorup2005}.
+The query time reduction is made possible by observing that binary search can be performed on the index sequence of the $dist_k(u)$ algorithm described in \cite{Thorup2005}.
 This is done by precomputing a secondary data structures $\mathcal{T}_u$ for each $u \in V$ in $O(k)$ time.
@@
 \section{Oracle with $O(\lg k)$ query time}
-As aforementioned, binary search on the iteration sequence of the Thorup-Zwick oracle is performed to drive down the query time to $\lg k$.
-Starting with the iteration sequence $\mathcal{I}=1,\hdots,k-1$, the idea is to identify $r=O(\lg k)$ subsequences $(\mathcal{I}_1=\mathcal{I}) \supset \mathcal{I}_1 \supset \hdots \supset \mathcal{I}_r$, where for $2 \leq j \leq t$ we have $|\mathcal{I}_{j-1}| \geq 2|\mathcal{I}_j|$.
+As aforementioned, binary search on the index sequence of the Thorup-Zwick oracle is performed to drive down the query time to $\lg k$.
+Starting with the index sequence $\mathcal{I}=1,\hdots,k-1$, the idea is to identify $r=O(\lg k)$ subsequences $(\mathcal{I}_1=\mathcal{I}) \supset \mathcal{I}_1 \supset \hdots \supset \mathcal{I}_r$, where for $2 \leq j \leq t$ we have $|\mathcal{I}_{j-1}| \geq 2|\mathcal{I}_j|$.
 We wish to maintain the invariant that $dist_k(u,v,i)$ applied to the first element of any subsequence $\mathcal{I}_j$ outputs the stretch $(2k-1)$ estimate in $|\mathcal{I}_j|$ time.
@@
 What lemmas \ref{lem:uvfeasterminates}, \ref{lem:basecase} and \ref{lem:uvfeasibility} entail is that, starting with the $(u,v)$-feasible sequence $\mathcal{I}=0,\hdots,k-1$, we may split it into two subsequences, one in which $(u,v)$-feasibility must be preserved.
-This splitting can be done recursively until a subsequence $\mathcal{I_r}$ for which $|\mathcal{I_r}|=O(\lg k)$ is determined.
-Applying $dist_k(u,v,i)$ to the first element of $\mathcal{I_r}$ produces a $(2k-1)$-approximation of the distance from $u$ to $v$ by $(u,v)$-feasibility in time proportional to $|\mathcal{I}_r|=O(\lg k)$.
+This splitting can be done recursively until a subsequence $\mathcal{I}_r$ for which $|\mathcal{I}_r|=O(\lg k)$ is determined.
+Applying $dist_k(u,v,i)$ to the first element of $\mathcal{I}_r$ produces a $(2k-1)$-approximation of the distance from $u$ to $v$ (by $(u,v)$-feasibility of $\mathcal{I}_r$) in time proportional to $|\mathcal{I}_r|=O(\lg k)$.
 
-\begin{figure}[h]
+The following theorem is the main result of \cite{Wulff2013}:
+\\
+\begin{thm}
+For an integer $k\geq 2$, a $(2k - 1)$-approximate distance oracle of G of size $O(kn^{1+1/k})$ and $O(\log k)$ query time can be constructed in $O\left( \min \left\lbrace kmn^{1+\frac{1}{k}}, \sqrt{k}m + kn^{1+c/k}\right\rbrace\right)$ time for some constant $c$.
+
+\paragraph{Proof.}
+
+For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
+The remaining preprocessing for $u$ is determining the necessary subsequences of $\mathcal{I}$ and the $j$ that maximized $\delta_j(u)$ for each subsequence.
+For a subsequence $I'=i_1,...i_2$, the necessary subsequences are constructed by finding an even index $i$ that equally splits $I'$ into two sets $i_1,...,i$ and $i,...,i_2$.
+Then, find a $j$ in $i_1,...,i$ that maximized $\delta_j(u)$.
+Then recurse on $i_1,...,i$ and $i,...,i_2$.
+The recursion stop when a subsequence has length at most $\log k$.
+This recursion corresponds to the recursion of $bdist_k$, and it will henceforth be referred to as the recursion of $bdist_k$.
+
+The query time is bounded by the number of recursions needed before reaching a $(u,v)-feasible$ subsequence of size at most $\log k$.
+$bdist_k$ uses binary search, to select and recurse on the $(u,v)$-feasible subsequence according to lemma \ref{lem:uvfeasibility}.
+As the number of recursions in this binary search is $O(\log k)$ and $i$ and $j$ are known for all subsequences, the query time is $O(\log k)$.
+
+The time to compute $j$ for all canonical subsequences using linear search requires $O(k\log k)$ time (an $O(k)$ search for each level of the recursion tree).
+This can be improved to $O(k)$ by precomputing a tree $\mathcal{T}_u$ in which each node is associated with a canonical subsequence corresponding to the recursion of $bdist_k$ on $\mathcal{I}$.
+Since the $bdist_k$ terminates when $|\mathcal{I}'| \leq \lg k$, we can stop the recursion when the subsequence associated with a leaf has size at most $\lg k$.
+Each node should contain the $j_{\mathcal{I}'}$ maximizing $\delta_{j_{\mathcal{I}'}}(u)$ for its subsequence $\mathcal{I}'$.
+The algorithm used to construct $\mathcal{T}_u$ determines $j_{\mathcal{I}'}$ for $\mathcal{I}'=i_1,\hdots,i_2$ in a bottom-up fashion by letting it attain the value of the maximum $j_{\mathcal{I_c}}$ for all children $\mathcal{I_c}$ on the path from the parent of the child containing $i_1$ to the parent of the child containing $i_2$, depicted in Fig.
+\ref{tree}.
+Such a traversal of $\mathcal{T}_u$ requires checking at most $O(\log k)$ subsequences.
+The path $P$ (red) starting in $p(l_1)$ and ending in $p(l_2)$ has $O(\log k)$ children, which we denote $X$.
+The union of $X$ clearly covers the entire subsequence $i_1,i_1+2,...,i_2-2,i_2$, and finding a $j$ that maximizes $\delta_j(u)$ in $X$ therefore gives a $j$ that maximizes $\delta_j(u)$ in the subsequence $i_1,...,i_2$.
+If $j$ is known for each node in $\mathcal{T}$, it follows that finding the desired $j$ for any canonical subsequences is bound by $O(\log k)$\\
+
+The recursion tree for $bdist_k$ for $u$ will have $\theta(k/\log k)$ children and $\theta(k/\log k)$ non-child nodes.
+Computing $j$ for each subsequence in $T$ will take $O(\log k)$ time per node, so total preprocessing time for $u$ is $O(k)$.
+Thus, the preprocessing time for finding $j$ for $G$ is $O(nk)\leq O(km)\leq O(kmn^{1/k})$ as desired.
+\end{thm}
+\begin{figure}[!hbt]
 \begin{tikzpicture}[level distance=1.5cm,
@@
 
-\begin{thm}
-For an integer $k\geq 2$, a $(2k - 1)$-approximate distance oracle of G of size $O(kn^{1+1/k})$ and $O(\log k)$ query time can be constructed in $O\left( \min \left\lbrace kmn^{1+\frac{1}{k}}, \sqrt{k}m + kn^{1+c/k}\right\rbrace\right)$ time for some constant $c$.
+\newpage
 
-\paragraph{Proof.}
+\bibliographystyle{plain}
+\bibliography{bibliography}
 
-For variable $k\geq 3$, for each $u$ the bunch $B_u$ in computed in $O(kmn^{2})$ using \cite{Thorup2005}.
-The remaining preprocessing for $u$ is determining the necessary subsequences of $\mathcal{I}$ and the $j$ that maximized $\delta_j(u)$ for each subsequence.
-For a subsequence $I'=i_1,...i_2$, the necessary subsequences are constructed by finding an even index $i$ that equally splits $I'$ into two sets $i_1,...,i$ and $i,...,i_2$.
-Then, find a $j$ in $i_1,...,i$ that maximized $\delta_j(u)$.
-Then recurse on $i_1,...,i$ and $i,...,i_2$.
-The recursion stop when a subsequence has length at most $\log k$.
-This recursion corresponds to the recursion of $bdist_k$, and it will henceforth be referred to as the recursion of $bdist_k$.
+\newpage
 
-The query time is bounded by the number of recursions needed before reaching a $(u,v)-feasible$ subsequence of size at most $\log k$.
-$bdist_k$ uses a binary search, so that at an arbitraty iteration the subsequence will be split in half into subsequences $i_1,...,i$ and $i,...,i_2$.
-Only the one of these two subsequences that is $(u,v)$-terminal is then recursed upon.
-As the number of recursions in this binary search is $O(\log k)$ and $i$ and $j$ are known for all subsequences, the query time is $O(\log k)$.
-To bound the time to identify these desired $j$, a simple linear search requires $O(k\log k)$ time.
-This can be improved to $O(k)$ by constructing of a recursive tree $\mathcal{T}_u$ for each $u$ that represents the recursion of $bdist_k$ on the subsequence $\mathcal{I}'$ consisting of all even numbers in $\mathcal{I}$.
-A bottom-up seach of $\mathcal{T}_u$ can identify for each canonical subsequence (canonical meaning it is a node in $\mathcal{T}$) $i_1,i_1+2,...,i_2$ an index $j$ in the subsequence that maximizes $\delta_j(u)$ in $O(k)$ time.
-The bottom-up traversal of $T$ requires checking at most $O(\log k)$ subsequences; consider the subsequence $i_1,..,i_2$ in seperate leaf nodes as seen in Fig.
-\ref{tree}.
-The path $P$ (red) starting in $p(l_1)$ and ending in $p(l_2)$ has $O(\log k)$ children, which we denote $X$.
-The union of $X$ clearly covers the entire subsequence $i_1,i_1+2,...,i_2-2,i_2$, and finding a $j$ that maximizes $\delta_j(u)$ in $X$ therefore gives a $j$ that maximizes $\delta_j(u)$ in the subsequence $i_1,...,i_2$.
-If $j$ is known for each node in $\mathcal{T}$, it follows that finding the desired $j$ for any canonical subsequences is bound by $O(\log k)$\\
-
-The recursion tree for $bdist_k$ for $u$ will have $\theta(k/\log k)$ children and $\theta(k/\log k)$ non-child nodes.
-Computing $j$ for each subsequence in $T$ will take $O(\log k)$ time per node, so total preprocessing time for $u$ is $O(k)$.
-Thus, the preprocessing time for finding $j$ for $G$ is $O(nk)\leq O(km)\leq O(kmn^{1/k})$ as desired.
-\end{thm}
-
+\appendix
+\section{Algorithms}
 \begin{Walgo}[ht]{20pt}
@@
 
-\bibliographystyle{plain}
-\bibliography{bibliography}
-
 \end{document}
